---
title: "Growth Rate Analysis"
output: html_notebook
---

This document is to compile the various measurements I have taken, for all genotypes in the competition experiment. The data from the fertilizer experiement is also included in this data set, but is properly integrated with the data pertaining to the fertilizer experiment in the document "FertilizerSynthesis.csv".

*Done*
###File for *initial size of GM and Maples, greenhouse location, treatment and competition number*: **"Data_collection_GH.csv"**. In R/masters_thesis

*Done*
###File for *germination transplant date, and gibberelic acid treatment*. **clean_germination_data_2.csv**. In R/masters_thesis.

*Done*
###File for *final manual measurement of maple size* **Maple_data.txt**. in Python/Raw_Data.

*Done*
###File for *final manual measurement of Alliaria leaf size* **Leaf_data.txt**. in Python/Final_GM_Data_CompetitionExp.

###File for *Growth Rate of Alliaria* **All_photo_data.txt**. in Python/python_pics_analysis.

*Done*
###File for *fern abundance and moss presence* **fern_cover.txt**. in Raw_Data. 

Note for analysis: 
only record as dead if I have the barcode, because some lost the barcode but did not die. Also, ferns were recorded for only one genotype if they were in the competition treatment, but it applied to both plants in the compeition treatment. 

*Done*
###File for *Pathogen damage* 

*Done*
###File for *Glocosinolate,Flavonoid and Chlorophyll content* **All_UV_Data.txt**. in masters_thesis/UVSpec

--------------------
--Goal of Analysis is to combine the documents into one master document that can be used to look at the data while considering all variables. 


#Incorporate Data_collection_GH_0.csv (treatment, ID, etc.) with Glucosinolate, Flavonoid and chlorophyll data (All_UV_Data.txt).
```{r}
library(dplyr)

#-------------------------------------------------------------------
#----------GH Data Prep
#-------------------------------------------------------------------

#read in GH data
dat=read.csv("Data_Moities/Data_collection_GH.csv",stringsAsFactors = F)

#Fix column names
colnames(dat)[9:12]<-c("comp_number","maple_leaf_length_0","maple_height_0","maple_leaves_0")

#Removing first row (Which contains no data).
dat<-dat[2:length(dat$gh_bench),]

#Remove maple controls (for now) This is because the strsplit is mis identifying the maple controls for garlic mustard data. I will have to fix this later.
dat<-dat[!grepl("aple",dat$Tag),]

#TO FIX
#The tag "c|MSMID1-1-20|Q|381" was mislabled as "c|MSMID1-1-20|G381". This is fixed below.
dat$Tag[grep("G381",dat$Tag)]<-"c|MSMID1-1-20|Q|381"





```


```{r}
#####
#Spec data prep--------------------------------------

#Importing functions created to clean up the UV spec data.
source("UVSpecProcessingModule.R")

##-----------------------------------

#Seperate spec data into Chlorophyll a and b
ChlorAB<-CleanData("Data_Moities/All_UV_Data.txt")[[2]]

#.... and Glucosinolate and flavonoid data
GF<-CleanData("Data_Moities/All_UV_Data.txt")[[1]]

```




#Sample Identification!
```{r}
#Using the Tag (fill ID) from the greenhouse data, assign a Tag to the ID numbers in the spec data.

#Glucosinolates and flavonoids.
for(i in 1:length(GF$Sample)){
  ID<-strsplit(GF$Sample[i],"_")[[1]][1]
  #Ensure the lable is surrounded by symbols, not numbers to ensure no faulty matches ... ex |4 cound be in |48, but not |4| in |48|
  ID<-paste("|",ID,"|",sep = "")
  GF$ID[i]<-ID
  count=0
  for(j in 1:length(dat$Tag)){
    #Modify tag locally to avoid mis matches. 
    locTag<-paste(dat$Tag[j],"|",sep="")
    if(grepl(ID,locTag,fixed=T)){
      GF$Tag[i]<-dat$Tag[j]
      count=count+1
    }
  }
  
  #Pool samples will be assigned a tag of simply "pool" and an ID of pool and date. 
  if (count==0){
    GF$Tag[i]<-GF$Sample[i]
    GF$Sample[i]<-paste(GF$Sample[i],GF$DataFile[i],sep="-")
  }
}


#Chlorophyll Samples
for(i in 1:length(ChlorAB$Sample)){
  ID<-strsplit(ChlorAB$Sample[i],"_")[[1]][1]
  ID<-paste("|",ID,"|",sep = "")
  ChlorAB$ID[i]<-ID
  count=0
  for(j in 1:length(dat$Tag)){
    locTag<-paste(dat$Tag[j],"|",sep="")
    if(grepl(ID,locTag,fixed=T)){
      ChlorAB$Tag[i]<-dat$Tag[j]
      count=count+1
    }
  }
   #Pool samples will be assigned a tag of simply "pool" and an ID of pool and date.  
  if (count==0){
    ChlorAB$Tag[i]<-ChlorAB$Sample[i]
    ChlorAB$Sample[i]<-paste(ChlorAB$Sample[i],ChlorAB$DataFile[i],sep="-")
  }
}

#-----------------------------------------
#Seperate GF into glucosinolate and flavonoid dataframes,these will be joined in a wide format. 

#Glucosinolate
gluc<-GF[GF$Compound=="gluc",]

#Flavonoid
flav<-GF[GF$Compound=="flav",]


#Making glucosinolate specific column names
colnames(gluc)<-paste("gluc",colnames(gluc),sep="_")

#Making flavonoid specific column names
colnames(flav)<-paste("flav",colnames(flav),sep="_")

#Removing controls from chlorophyll
ChlorNoCont<-ChlorAB[ChlorAB$ID!="|cont|",]

ChlorNoCont[grepl("Feb_13",ChlorNoCont$DataFile),]





```

#Removing Duplicates and checking for errors. 
```{r}

#Searching for those with more replicates than they should have. They should have 2 because each leaf has two technical replicates. For some reason, the same sample is appearing for those that should not have more than 1 sample per leaf (i.e. those not in the fertilizer treatment)
errors<-gluc %>% group_by(gluc_Sample) %>% summarize(n=n()) %>% filter(n>2)
errors<-errors[!grepl("i",errors$gluc_Sample),]

#Datafile containing the errors... I must go through each one and check it. they will be deleted, not averaged if there is a duplicate. 
errors<-gluc %>% select(gluc_Sample,gluc_DataFile,gluc_Tag,gluc_Conc) %>% right_join(errors,by="gluc_Sample") %>% filter(gluc_Tag!="pool")



# I went through these errors and could not explain them. I believe these errors were brought about because of poor transcribing during the data collection  process. This is unfortunate, but they must be deleted from the analysis because i an unsure of which sample is the correct sample and which is the transcribing error. This is done in the next chunk.

```


#Averaging duplicates (i.e. technical replicates) 
```{r}
#gluc
Average_gluc<-gluc %>% group_by(gluc_Sample) %>% summarize(gluc_Conc=mean(gluc_Conc))


#flav
Average_flav<-flav %>% group_by(flav_Sample) %>% summarize_at(.vars = vars(flav_Conc),.funs=mean)

#ChlorNoCont
Average_ChlorNoCont<-ChlorNoCont %>% group_by(Sample) %>% summarize_at(.vars=vars(ChlorA,ChlorB),.funs=mean)

#-----
#Add in missing columns

#Remove duplicates, this is so that other columns in the chlorophyll data frame can be aded back in. #the column Datafile, is no longer relevant for fertilizer files as samples were averaged over multiple datafiles. 
Col_Merger0.1<-ChlorNoCont[!duplicated(ChlorNoCont$Sample),]
#Select relevant columns
Col_Merger<-Col_Merger0.1 %>% select(Sample,Tag,DataFile)

#Check to ensure that the merge went okay and no values were lost. 
if(length(Col_Merger$Sample)!=length(Average_ChlorNoCont$Sample)){
  stop("Columns mismatch in the merge of chlorophyll factor columns with chlorophyll data columns.")
}

#Merging dataframs.
Average_ChlorNoCont2<-left_join(Average_ChlorNoCont,Col_Merger,by="Sample")


#------
#Merge all three dataframes into a wide format. 
All_Wide0.1<-left_join(Average_ChlorNoCont2,Average_gluc,by=c("Sample"="gluc_Sample"))
All_Wide<-left_join(All_Wide0.1,Average_flav,by=c("Sample"="flav_Sample"))

#Check to ensure it was done correctly: 
if(length(All_Wide$Sample)!=length(Average_ChlorNoCont$Sample) |length(All_Wide$Sample)!=length(Average_gluc$gluc_Sample)
|length(All_Wide$Sample)!=length(Average_flav$flav_Sample)){

  stop("gluc, flav and chlorophyll samples did not match upafter duplicates were averaged.")
}


#removing errors found in the previous chunk. Sample size reduced from 1108 to 1093
All_Wide<-All_Wide %>% filter(!Tag %in% errors$gluc_Tag)



```


#--------Taking care of mismatching Tag/ID!!!!
```{r}

#a273_2_dupl is a|KVEDG1-1-80|Q|273 and shares a number with d|JBCHY1-1-50|Q|273. Because of the a identifier, i am assiging this plant to a|KVEDG1-1-80|Q|273. "da" stands for duplicate A

#Leaf one
All_Wide$Tag[All_Wide$Tag=="a273_1"]<-"a|KVEDG1-1-80|Q|273"
All_Wide$Sample[All_Wide$Sample=="a273_1-Dat_Jan_17_2020_PM.txt"]<-"273da_1"

#Leaf two 
All_Wide$Tag[All_Wide$Tag=="a273_2_dupl"]<-"a|KVEDG1-1-80|Q|273"
All_Wide$Sample[All_Wide$Sample=="a273_2_dupl-Dat_Dec_6_2019.txt"]<-"273da_2"




#d273_JBCHY_1_dup is the second duplicate from above. It will be changed to d|JBCHY1-1-50|Q|273 "dd" stand for duplicate "d". - this is because of the germination treatment.

#Leaf 1
All_Wide$Tag[All_Wide$Tag=="d273_JBCHY_1_dup"]<-"d|JBCHY1-1-50|Q|273"
All_Wide$Sample[All_Wide$Sample=="d273_JBCHY_1_dup-Dat_Dec_9_2019.txt"]<-"273dd_1"

#Leaf 2
All_Wide$Tag[All_Wide$Tag=="d273_Jbchy_2"]<-"d|JBCHY1-1-50|Q|273"
All_Wide$Sample[All_Wide$Sample=="d273_Jbchy_2-Dat_Jan_17_2020_PM.txt"]<-"273dd_2"

#b?wsswm3-1-0_2 is unknown because we did not record the number.There is one genotype which is actually named "b|WSSWM3-1-0|?" Let us see if it is this genotype that is missing from All_Wide..
All_Wide<-All_Wide[!All_Wide$Tag=="b?wsswm3-1-0_2",]
All_Wide<-All_Wide[!All_Wide$Tag=="b?wsswm3-1-0_dup",]


#"e?JBCHY_dup" Belongs to the genotype "e|JBCHY1-1-50|?". This will be modified. 
All_Wide$Tag[All_Wide$Tag=="e?JBCHY_dup"]<-"e|JBCHY1-1-50|?"




#Sample 381 is listed as G381, which is why it was not identified, i will change it to be appropriate

All_Wide[All_Wide$Sample=="381_1-Dat_Jan_21_2020_AM.txt",]<-"381_1"

All_Wide[All_Wide$Tag=="381_1",]<-"c|MSMID1-1-20|G381"



```




#Final Merging of clean greenhouse data and clean UV data with duplicates averaged.
```{r}

#This left join will keep all individuals that we have glucosinolate and flavonoid data on. 
Final<-left_join(All_Wide,dat,by="Tag")

Final<-Final %>% select(-new._code_needed.,-Helper.date)


#Check for those that did not get properly identified. 
Final[is.na(Final$gh_bench)&Final$Tag!="pool",]


write.csv(Final,"DataSynthesis.csv")



```

The output above will be empty if all labels were matched correctly. Else there will be a dataframe containing the samples that were not matched. 


Integrating
###File for *fern abundance and moss presence* **fern_cover.csv**. in Raw_Data.

```{r}
#Clear Environment. 
rm(list=ls())

library(dplyr)


#Read in data
dat<-read.csv("Data_Moities/fern_cover.csv",stringsAsFactors = F)

#dat<-dat[!grepl("aple",),]
final0.1<-read.csv("DataSynthesis.csv",stringsAsFactors = F)

#Modyfiyng tag to match final document. 
dat$Genotype<-gsub("\\","|",dat$Genotype,fixed=T)
dat$Genotype<-gsub("/","-",dat$Genotype,fixed=T)

#Modifying column names to match final document.
colnames(dat)[1]<-"Tag"

#Genotype "e|SMITH1-1-0|Q|i159" was entered twice into the fern datasheet. As there is no way to assign an identity, and fern data are ratically different (i.e. 1 vs 15). This will be treated as a NA unless evidence for an ID arises. 
dat[dat$Tag=="e|SMITH1-1-0|Q|i159",c("Moss.tf","Fern")]<-NA

#Removing the duplicate
dat<-dat[!duplicated(dat$Tag),]

#Joining
final<-left_join(final0.1,dat,by="Tag")


#Those that we did not enter must be made to zero for both. 
for(i in 1:length(final$Fern)){
  if(is.na(final$Fern[i])){
    final$Moss.tf[i]<-"n"
    final$Fern[i]<-0
  }
  else next
}

if(colnames(final)[1]=="X"){
  final<-select(final,-X)
}


write.csv(final,"DataSynthesis.csv")


```





Removing Runs from dec 8 and 9. These runs were performed before the evaporation step was integrated into the protocol. Also, glucosinolate and flavonoid data from Jan 30 PM, Jan 31 AM and Jan 31 PM will be removed. These runs were performed on a different plate as the old plate was becomming quite stained. These runs had very low pools with much more variance, and thus the glucosinolate and flavonoid values need to be removed as the data is not reliable.The chlorophyll data for these runs is, however, okay because the chlorophyll samples were performed on the same plate. In Mabels run on feb 3 2020 AM, she added twice the amount of stain by mistake.(I.e. final samples were 300ul instead of 200, beause she added 100ul of CHCOOH and ALCL3 instead of 50ul of each). For this reason flavonoids will be removed from this run. 
```{r}
rm(list=ls())
library(dplyr)
dat<-read.csv("DataSynthesis.csv",stringsAsFactors = F)




#Removing all data from runs on Dec 6 2019 and Dec 8 2019 
dat<-dat[dat$DataFile!="Dat_Dec_6_2019.txt"& dat$DataFile!="Dat_Dec_8_2019.txt",]



#Removing only glucosinolate and flavonoid runs from Dat_Jan_30_2020_PM.txt, Dat_Jan_31_2020_AM.txt, Dat_Jan_31_2020_PM.txt
dat[dat$DataFile=="Dat_Jan_30_2020_PM.txt" | dat$DataFile=="Dat_Jan_31_2020_AM.txt"| dat$DataFile=="Dat_Jan_31_2020_PM.txt",c("gluc_Conc","flav_Conc")]<-NA



#Visualizing Mables Run
Feb3Pool<-dat$flav_Conc[dat$DataFile=="Dat_Feb_3_2020_AM.txt" & dat$Tag=="pool"]
OtherPool<-dat$flav_Conc[dat$DataFile!="Dat_Feb_3_2020_AM.txt" & dat$Tag=="pool"]
boxplot(Feb3Pool,OtherPool)

#Removing Flavonoid data from Mabels Run on Feb 3rd 2020 AM.
dat$flav_Conc[dat$DataFile=="Dat_Feb_3_2020_AM.txt" ]<-NA

####---------------------------


#Selecting relevant columns
dat<-dat %>% select(Sample:Fern)

library(ggplot2)



#####
#Visualizing data So far
####
  
#Making a column for the pools to check them out. 
dat$Pool[dat$Tag=="pool"]<-"Yes"
dat$Pool[dat$Tag!="pool"]<-"No"


#Glucosinolate
ggplot()+
  geom_boxplot(aes(y=as.numeric(dat$gluc_Conc),x=as.factor(dat$Pool)))

#Flavonoid
ggplot()+
  geom_boxplot(aes(y=as.numeric(dat$flav_Conc),x=as.factor(dat$Pool)))

#ChlorA
ggplot()+
  geom_boxplot(aes(y=as.numeric(dat$ChlorA),x=as.factor(dat$Pool)))

#ChlorB
ggplot()+
  geom_boxplot(aes(y=as.numeric(dat$ChlorB),x=as.factor(dat$Pool)))

#Quick look at the gluc and flav data. 
hist(as.numeric(dat$gluc_Conc))
hist(as.numeric(dat$flav_Conc))


#[dat$DataFile=="Dat_Feb_6_2020_AM.txt" & dat$Tag=="pool"]

write.csv(dat,"DataSynthesis.csv")




```




#Account for sampling differences amoung days using the pool data. 
#Determine if the simple relationship with of subtracint the control data from the stain data is adequate. I have reason to believe that it may not be a 1:1 relationship. 
ggplot(glucPool)+
  geom_point(aes(x=gluc_ControlData,y=gluc_StainData))+
  geom_abline(intercept=0.680,slope=0.7648)

lm(gluc_StainData~gluc_ControlData,data=glucPool)

hist(glucPool$gluc_Conc)











###File for *final manual measurement of Alliaria leaf size*
**Pathogen_Damage_Manual.csv** is the data file containing the holepunched leaf data, along with pathogen damage. 
**Gm_Final_Leaf_data.txt** is the data pertaining to the rest of the leaves. 
```{r}
#This file contains the length and width of every leaf in the competition treatment that did not have a whole punch. This data has a complementary set of photos of each leaf that was holepunched, along with the length and width of each holepunched leaf. This, together, can be used to determine how leaf size affects secondary compound production, but can also be amalgamated into a final biomass measurement. 

rm(list=ls())

#File to be integrated.
main<-read.csv("DataSynthesis.csv")

if(colnames(main)[1]=="X"){
  main<-select(main,-X)
}






#Clear Environment. 
dat<-read.csv("Data_Moities/Gm_Final_Leaf_data.txt",header = T)
datP<-read.csv("Data_Moities/Pathogen_Damage_Manual.csv",header = T)


#------------
#Fixing Genotype barcodes
#------------

#DatP (Punched leaves)
datP$Genotype<-gsub("ยง","|",datP$Genotype)
datP$BlackPathDam<-as.numeric(datP$BlackPathDam)
datP$ThripsDam<-as.numeric(datP$ThripsDam)
datP$GM_Leaf_Len<-as.numeric(gsub("\\D","",datP$GM_Leaf_Len))
datP$GM_Leaf_Wid<-as.numeric(gsub("\\D","",datP$GM_Leaf_Wid))
datP$GM_Leaf_Number<-as.numeric(gsub("\\D","",datP$GM_Leaf_Number))


#Dat (non- punched leaves)
dat$Genotype<-gsub("ยง","|",dat$Genotype)
dat$GM_Leaf_Len<-as.numeric(gsub("\\D","",dat$GM_Leaf_Len))
dat$GM_Leaf_Wid<-as.numeric(gsub("\\D","",dat$GM_Leaf_Wid))
dat$GM_Leaf_Number<-as.numeric(gsub("\\D","",dat$GM_Leaf_Number))

#------------
# Full body size
#------------

#Finding the total leaf length and and width
tempSize<-rbind(dat,datP[1:4])

#Area Calculation of each leaf. 
tempSize$GM_Leaf_Area<-tempSize$GM_Leaf_Len*tempSize$GM_Leaf_Wid

#Summarizing total leaf area for each genotype and recording the number of leaves. 
tempArea<-tempSize %>% group_by(as.factor(Genotype)) %>% summarize_at(vars(GM_Leaf_Area,GM_Leaf_Number), .funs=list(~sum(.),~max(.)))
colnames(tempArea)[1]<-"Genotype"

#Merging the whole plant data with the leaf punch data. 
final0.1<-left_join(datP,tempArea,by="Genotype")

#Removing irrelevant columns
final0<-final0.1 %>% select(-GM_Leaf_Number_sum,-GM_Leaf_Area_max)
colnames(final0)[colnames(final0)=="GM_Leaf_Area_sum"]<-"GM_TotalLeaf_Area"
colnames(final0)[colnames(final0)=="GM_Leaf_Number_max"]<-"GM_NumberOfLeaves"

#Joining the synthesis data with the new data on leaf size and pathogen damage based on the ID number, which consists of the plant ID and the leaf number
final0$Sample<-paste(gsub(".*\\|","",final0$Genotype),final0$GM_Leaf_Number,sep = "_")



#Mergining clean data with "Synthesis" dataframe.
final0 <-final0 %>% select(-Genotype)

final<-left_join(main,final0,by="Sample")


#Clarifying the names in the dataframe. 
colnames(final)[colnames(final)=="leaf_length"]<-"GM_Leaf_Len_Initial"
colnames(final)[colnames(final)=="true_leaves"]<-"GM_NumberOfLeaves_Initial"



#Writing csv
write.csv(final,"DataSynthesis.csv")


```



###File for *Growth Rate of Alliaria* 
```{r}
#Need to integrate the estimated growth rate parameters. 
```



##Insert Final Maple biomass and Data on the Control Maples - both initial and final measurements. 
```{r}
library(dplyr)
rm(list=ls())
#------------------------------
#Integrating initial maple control measurements.... initial values of maples in treatments are already in the data. 
#read in GH data
dat=read.csv("Data_Moities/Data_collection_GH.csv",stringsAsFactors = F)

#Fix column names
colnames(dat)[9:12]<-c("comp_number","maple_leaf_length_0","maple_height_0","maple_leaves_0")


#Removing first row (Which contains no data).
dat<-dat[2:length(dat$gh_bench),]

#Isolate maple controls 
dat<-dat[grepl("aple",dat$Tag),]

#Select relevant columns. 
CntrZero<-dat %>% select(Tag,treatment,maple_leaf_length_0,maple_height_0,maple_leaves_0)


#------------------------------
#Integrating final maple measurements, controls and in competition. 
MapDat<-read.csv("Data_Moities/Maple_data.txt",header=F,stringsAsFactors = F)

#Creating column names
colnames(MapDat)<-c("Nothing","Tag","Leaf","Length","Width","Damage","SampleTime","StemHeight")


#Replacing Characters in Tag Column. 
MapDat$Tag<-gsub("ยง","|",MapDat$Tag,perl = F)

#Removing strings from numeric columns. 
MapDat$Length<-gsub("\\D","",MapDat$Length)
MapDat$Width<-gsub("\\D","",MapDat$Width)
MapDat$StemHeight<-gsub("\\D","",MapDat$StemHeight)
MapDat$Leaf<-gsub("\\D","",MapDat$Leaf)


#Fixing genotype labels. 
#DVGM-20|Q|117 has a genotype lable of "b" in the main synthesis file, but it is "c" here. I will change it in the final maple data file and take the main file as correct.
MapDat$Tag[MapDat$Tag=="c|DVGM-20|Q|117"]<-"b|DVGM-20|Q|117"




#Replacing Damage with a 1 for yes and 0 for no, so that i can take the mean. This will represent the percent of damaged leaves on the plant. 
MapDat$Damage[MapDat$Damage=="damage-n"]<-0
MapDat$Damage[MapDat$Damage=="damage-y"]<-1

#making columns numeric. 
class(MapDat[,3])<-"numeric"
class(MapDat[,4])<-"numeric"
class(MapDat[,5])<-"numeric"
class(MapDat[,6])<-"numeric"
class(MapDat[,8])<-"numeric"
class(MapDat[,2])<-"Factor"


#Making a leaf area column. 
MapDat$Area<-MapDat$Length*MapDat$Width

#Summarizing data on the whole plant. 
MapFinal<-MapDat %>% group_by(Tag) %>% summarize_at(vars("Leaf","Length","Width","Damage","StemHeight","Area"),.funs = list(~max(.),~sum(.),~mean(.)))

#Selecting relevant columns
MapFinal<-MapFinal %>% select(Tag,Leaf_max,Length_mean,Width_mean,Damage_mean,StemHeight_max,Area_sum,Area_mean)



#Modyfying names to be appropriate. 
colnames(MapFinal)[-1]<-paste("Maple",colnames(MapFinal)[-1],"End",sep = "_")
colnames(MapFinal)[2]<-"Maple_LeafNum_End"


#---------------------------
#Reading in the synthesis file to integrate these data. 
Synth<-read.csv("DataSynthesis.csv")
Synth<-Synth %>% select(-X)


#--------------------------
#Integrating
#Integrating Controls into one dataframe.
ControlFinal<-left_join(CntrZero,MapFinal[grepl("aple",MapFinal$Tag),],by="Tag")
#Integrating final maple data into the original synthesis file, which lack maple controls. 
SynthFinal<-left_join(Synth,MapFinal[!grepl("aple",MapFinal$Tag),],by="Tag")


#Integrating control data into the final data frame. 
#Creating a dataframe identical to the synthesis dataframe, but containing the maple data. 
Blank<-SynthFinal[1:31,]#Assigning column names from synth data frame
Blank[1:31,]<-NA #Making them all NA.
Blank$Tag<-ControlFinal$Tag
Blank$treatment<-ControlFinal$treatment
Blank$maple_leaf_length_0<-ControlFinal$maple_leaf_length_0
Blank$maple_height_0<-ControlFinal$maple_height_0
Blank$maple_leaves_0<-ControlFinal$maple_leaves_0
Blank$Maple_LeafNum_End<-ControlFinal$Maple_LeafNum_End
Blank$Maple_Length_mean_End<-ControlFinal$Maple_Length_mean_End
Blank$Maple_Width_mean_End<-ControlFinal$Maple_Width_mean_End
Blank$Maple_StemHeight_max_End<-ControlFinal$Maple_StemHeight_max_End
Blank$Maple_Area_sum_End<-ControlFinal$Maple_Area_sum_End
Blank$Maple_Area_mean_End<-ControlFinal$Maple_Area_mean_End

#Merging maple control data with the master dataframe. 
Final<-rbind(SynthFinal,Blank)
Final
#Writing to file. 

write.csv(Final,"DataSynthesis.csv")

#Are some maples missing data from the beggining? 
#dat2[is.na(dat2$Maple_Length_mean_End)&!is.na(dat2$maple_height_0),]
```

#Insert Germination date and germination treatment. 
```{r}
rm(list=ls())
#Read in germination data
dat<-read.csv("Data_Moities/clean_germination_data_2.csv",stringsAsFactors = F)
dat<-dat %>% select(-X.1,-X)

#Read in master data frame. 
master<-read.csv("DataSynthesis.csv")
master <- master %>% select(-X)

#I was planning on using the date moved in the analysis, but i decided not to because it may not represent the date that the plant germinated, and because the same plate continued to germinate and was moved up to three times, making it not possible to identify the exact date that any given plant was moved into the growing chamber. For certain genotypes, i actually recorded the length of each hypocotyle that was moved. It is unfortunate to not use this data. 

#Selecting relevant columns. 
dat<-dat %>% select(Petri.Dish,GA3)

#Cleaning up the column GA3
dat$GA3[!grepl("y",dat$GA3)]<-"n"

#Merging the dataframes. 

master$GA3<-NA
for(i in 1:length(dat$Petri.Dish)){
  #finding all tags in the master data frame corresponding to the petri dish plate at i. 
 master$GA3[grepl(dat$Petri.Dish[i],master$Tag,fixed=T)]<-dat$GA3[i]
}

write.csv(master,"DataSynthesis.csv")

```



