---
title: "Competitive Ability and the influence of glucosinolates and flavonols"
author: "Richard Honor"
date: "31/03/2020"
output: html_document
---

#Read in and prep data
```{r}
library(ggplot2)
library(dplyr)
library(lmerTest)
library(car)
library("glmmTMB")


#read in data
rm(list=ls())
dat<-read.csv("DataSynthesis.csv")

#Assign family column
prefamily<-gsub("*.\\|","",dat$Tag)
dat$Family<-gsub("\\-.*","",prefamily)

#remove those with fertilizer treatment, and extra genotypes that are only in the alone treatment. 
dat<-dat[!grepl("i",dat$Sample,fixed=T),]


#Function to weigh pathogen damage by leaf area. 
Weigh<-function(x){
  x/(dat$GM_Leaf_Len*dat$GM_Leaf_Wid)
}
dat$BlackPathDamW<-Weigh(dat$BlackPathDam)
dat$ThripsDamW<-Weigh(dat$ThripsDam)
dat$WhiteFungDamW<-Weigh(dat$WhiteFungDam)


#Average Duplicates. 
dat2<-dat %>% select(-X) %>% group_by(Tag) %>%  summarize(gh_col=first(gh_col),gh_bench=first(gh_bench),treatment=first(treatment),GA3=first(GA3),Family=first(Family),Maple_StemHeight_End=mean(Maple_StemHeight_End),Maple_LeafNum_End=mean(Maple_LeafNum_End),maple_leaf_length_0=mean(maple_leaf_length_0),maple_leaves_0=mean(maple_leaves_0),Maple_TotalLeafArea_End=mean(Maple_TotalLeafArea_End),MapleDamage=mean(Maple_Damage_End),Fern=first(Fern),gluc_Conc=mean(gluc_Conc),flav_Conc=mean(flav_Conc),maple_height_0=mean(maple_height_0),ChlorA=mean(ChlorA), GM_TotalLeaf_Area=first(GM_TotalLeaf_Area),ThripsDam=mean(ThripsDam),BlackPathDam=mean(BlackPathDam),WhiteFungDam=mean(WhiteFungDam),BlackPathDamW=mean(BlackPathDamW),ThripsDamW=mean(ThripsDamW),WhiteFungDamW=mean(WhiteFungDamW))

dat
#Converting white fungal damage to logistic. 
dat2$WhiteFungLogis<-NA
dat2$WhiteFungLogis[dat2$WhiteFungDam>0]<-"Yes"
dat2$WhiteFungLogis[dat2$WhiteFungDam==0]<-"No"




```

#Creating a maple dataframe. 
```{r}
Maple<-dat2[dat2$treatment=="m"|dat2$treatment=="mcnt",]

Maple[is.na(Maple$Maple_StemHeight_End),]

#b|EFCC2-4-80|Q|144 and f|JBCHY1-1-50|Q|247,e|CBMCK1-1-0|N|49, e|JWBOY-2-80|Q|264 are simply not in the datafile. Nothing to do there - they will be deleted from the analyis. These genotypes are either dead, or we missed them when conducting the sampling.
Maple<-Maple[!is.na(Maple$Maple_StemHeight_End),]
Maple$treatment<-factor(Maple$treatment,levels = c("m","mcnt"))




```

#Maple PCA 
```{r}
#PCA values are based on the standard deviations of the variables included in the analysis. Therefore, it is neccessairy to scale the variables before using them in a PCA. Variables with high SD will have more weight in constructing the loadings than a variable with a low SD. I need all variables to have the same standard deviation. 
Standardize<-function(x){
  standard<-(x-mean(x,na.rm=T))/sd(x,na.rm=T)
}

#Selecting variables to use in the PCA (All initial and final maple measurements which could indicate performance)
PCAMaple<-Maple %>% select(maple_height_0,maple_leaf_length_0,maple_leaves_0,Maple_StemHeight_End,Maple_LeafNum_End,Maple_TotalLeafArea_End)

#Standardizing all variables.
PCAMaple<-data.frame(apply(PCAMaple,2,Standardize))

#---------------
#Performing model 
#---------------

#Model with everything
pcaModelTotal<-prcomp(PCAMaple)

#All variables go in the same direction.
biplot(pcaModelTotal)

#40% of the variation in the data is explained in the first PCA. 
summary(pcaModelTotal)

#All variables are correlated with the PC1 loading. 
plot(predict(pcaModelTotal)[,1]~PCAMaple$Maple_TotalLeafArea_End)
plot(predict(pcaModelTotal)[,1]~PCAMaple$maple_height_0)
plot(predict(pcaModelTotal)[,1]~PCAMaple$maple_leaf_length_0)
plot(predict(pcaModelTotal)[,1]~PCAMaple$maple_leaves_0)
```

#Examinging differences in maple performance, while controlling for the initial maple size. 
```{r}


#Adding in PC1 vales from the pca. This will be used to control for initial maple size in my experiment. 
Maple$PC1Tot<-predict(pcaModelTotal)[,1]


#Modelling
fitTreat<-lm(Maple_TotalLeafArea_End~PC1Tot+treatment,data=Maple)
summary(fitTreat) #This is highly significant effect of treatment.... 

fitTreatInt<-lm(Maple_TotalLeafArea_End~PC1Tot*treatment,data=Maple)
anova(fitTreat,fitTreatInt)#The interaction term is significant. 
summary(fitTreatInt)


#
ggplot(Maple)+
  geom_point(aes(y=Maple_TotalLeafArea_End,x=PC1Tot,colour=treatment))

#The conclusion is that, not only are maples in the mcnt treatment have higher fitness after controlling for differences in initial size, they also exhibit increased growth at a given body size. 
```

# Modelling: Competitive ability 
```{r}
#The influence of family, glucosinolates and flavonoids on competitive ability
hist(Maple$Maple_TotalLeafArea_End,breaks=50)
#There is a limit at zero, so this is not a true normal distribution. It resembles a reverse gaussian distribution except this distribution has values at zero, infact it is slighly zer inflated for the distibution. Therefore i think a tweedie distibution is best. 

#Removing maple controls (to be used in models that do not include controls) 
MapleModel<-Maple %>% filter(treatment=="m")


#Modelling: Maple performance predicted by PC1 and gluc Conc, Maple Damage, Family and gh location. What are the significant random effects?
fitTwFull<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+gluc_Conc+MapleDamage+(1|Family)+(1|gh_bench),family = tweedie, data=MapleModel)

fitTwFull0.1<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+gluc_Conc+MapleDamage+(1|gh_bench),family = tweedie, data=MapleModel)

fitTwFull0.2<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+gluc_Conc+MapleDamage+(1|Family),family = tweedie, data=MapleModel)

fitTwFull0.3<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+gluc_Conc+MapleDamage,family = tweedie, data=MapleModel)

anova(fitTwFull,fitTwFull0.1,fitTwFull0.2,fitTwFull0.3) #It is not important to include random effects, therefore, I will not. I am not including flav_conc because i did not find evidence that it was in the roots. 


#What are the significant fixed effects?


fitTw1<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot*gluc_Conc+MapleDamage,family = tweedie, data=MapleModel)
summary(fitTw1) #The interaction is not important, but glucosinolate concentration and maple damage are. 

fitTw2<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+gluc_Conc+MapleDamage,family = tweedie, data=MapleModel[!is.na(MapleModel$gluc_Conc),])
summary(fitTw2)
 #Glucosinolate concentration and MapleDamage are both highly significant. The p valaues in the summary() function are p values by exclusion, and represent likelyhood ratio p values of models excluding only that variable. 



#The question is, however, do glucosinolates significant reudce maple performance  because they are inhibiting maple (allelopathy) OR because those with high glucosinolate expression are better competitors and aquire more resources to then allocate more resources to defenes? (Chicken or the egg)

#Is the negative effect of glucosinolates on maple performance removed once Chlorophyll A expression is added to the model? This would control for garlic mustard performance becuase those that produce more chlorophyll can also produce more glucosinolates. 
fitTw3<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+MapleDamage+gluc_Conc+ChlorA,family = tweedie, data=MapleModel)
summary(fitTw3)
# Including Chlorophyll A completely removed the effect of glucosinolates. This suggests that glucosinolates may be correlated with maple performance due to plants that reudce maple performance having higher fitness and more resources for glucosinolates without glucosinolates actually being responsible. On the other hand, those with more glucosinolates may have higher fitness and be able to produce more Chlorophyll A because they are inhibiting maple.


#Checking Model Assumptions. 
summary(fitTw2)
plot(resid(fitTw2))
hist(resid(fitTw2),breaks=20)#Looks reasonably normal to me.

fitV<-lm(Maple_TotalLeafArea_End~PC1Tot+MapleDamage+gluc_Conc+ChlorA,data=MapleModel)

vif(fitV) #Vif for ChlorA and gluc concentration are both below 2. This suggest that gluc_Conc and Chlor concentration are not high enough that the effect of the two are indistinguishable. This suggests that the entire effect of glucosinolates is due to chlorophyll concentration. 


#Permutation test to check the reliability of the p values in the best model.
fitTw3<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+gluc_Conc+MapleDamage,family = tweedie, data=MapleModel)

summary(fitTw3)$coef
datPerTest<-MapleModel
zStore<-c()
for(i in 1:500){
  #Randomize flavonoid concentration.
  datPerTest$gluc_Conc<-sample(datPerTest$gluc_Conc,length(datPerTest$gluc_Conc),replace = F)
  
  #Run Model with randomized flavonoid concentration and extract test statistic
  glucZval<-summary(update(fitTw3,data=datPerTest))$coef[[1]][3,3]
  
  #Store z value.
  zStore[i]<-glucZval
}

sum(zStore<=-2.883)/length(zStore)

#The simulated p value was 0.002, which is close to the observed value of 0.004. This is a reliable model. 

```


#Is there evidence that those in the maple and garlic mustard treatment have the same relationship between glucosinolate and chlorA? If glucosinolates are truly beneficial in one treatment but not in another, we might expect for the relationship between glucosinolates and ChlorA to be stronger in the treatment in which glucosinolates are beneficial. This is because if those that create more chlorophyll a passively allocate more resources to glucosinolates, this relationship may be a weaker relationship than if glucosinolates are increasing fitness and allowing an increased allocation to chlrophyll A. 
```{r}
fit<-lm(gluc_Conc~ChlorA*treatment,data=dat2)
fit2<-lm(gluc_Conc~ChlorA+treatment,data=dat2)
anova(fit,fit2)
#There is a significant interaction.....
summary(fit)
 
 
dat2plot<-dat2 %>% filter(treatment!="mcnt")
dat2plot$treatment<-droplevels.factor(dat2plot$treatment)

ggplot(dat2plot)+
  geom_point(aes(x=ChlorA,y=gluc_Conc,colour=treatment))+
  geom_abline(slope = 0.37149,intercept = 0.84767,colour="#009E73")+#alone
  geom_abline(slope = 0.37149+0.21832,intercept = 0.84767-0.09537,colour="#56B4E9")+#gm
  geom_abline(slope = 0.37149+0.21136,intercept = 0.84767-0.09984,colour="#E69F00")+#maple
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00","black"),labels=c("Alone","Garlic Mustard","Maple"))

#This demonstrates that the relationship between glucosinolate and chlorophyll is steeper in the treatments with competition. Therefore, there may be a benefit to producing glucosinolates in the competition treatments? Those with high glucosinolates in the maple treatment have higher chlorophyll levels than those with high glucosinolates in the alone treatment. In other words, those in the competition treatment have lower levels of chlorophyll at low levels of glucosinolates, and have higher level of chlorphyll at higher levels of glucosinolates. In other words (again) glucosinolates may be increasing performance in the competition treatments. 
```


#Effect of maple on GM performance. 
I chose to seperate this model from the last due to the causality inherent in this data. Glucosinolate concentration should affect garlic mustard fitness only through effects on maple and pathogen abundance. Including glucosinolate concentration in a model with both of these variables to determien the effect of glucosinolates on fitness is actually determining how much glucosinolates affect fitness when these terms are controlled for, which should be not at all. Therefore multiple models are needed to test if glucosinolates influence abundance of pathogens and maple performance, after controlling for garlic mustard performance (Using chlorophyll A, because those with high performance might simply be making more glucosinolates). Then i can see how much maple and pathogens influence garlic mustard performance. 
```{r}
#There is an odd distribution of leaf size, but it is fairly normal. 
hist(MapleModel$GM_TotalLeaf_Area,breaks=25)

#What effect does maple have on garlic mustard performance? 
MapleModel
#Standardizing maple size, as it is now a predictor variable is has too large of a SD and was messing up the model. 
MapleModel$Maple_TotalLeafArea_End<-Standardize(MapleModel$Maple_TotalLeafArea_End)



#MaxModel (I predict possible interactions between pathogens, because the infection of one pathogen could make others worst and decrease fitness more when infected with more than one pathogen, however i expect competitive effects of fern and maple total leaf area to only be additive because elimiting nutrients would not have any forseeable compounding effects. It should be noted that glucoisnolate concentration is not in the model, as explained above)

#Modelling random effects 
fit<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDam*BlackPathDam*WhiteFungLogis+(1|Family)+(1|gh_bench/gh_col),data=MapleModel)

fit2<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDam*BlackPathDam*WhiteFungLogis+(1|Family)+(1|gh_bench),data=MapleModel)

fit3<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDam*BlackPathDam*WhiteFungLogis+(1|gh_bench/gh_col),data=MapleModel)

#Is collumn important?
anova(fit,fit2) #Yes it is. 

#Is family important? 
anova(fit,fit3) #No, it is just on the verge of significance (p=0.058)


#Modeling fixed effects: 

fit<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDam*BlackPathDam*WhiteFungLogis+(1|gh_bench/gh_col),data=MapleModel)

fit2<-update(fit,~.-ThripsDam:BlackPathDam:WhiteFungLogis)
anova(fit,fit2) #Not a significant three way interaction although it is close (p=0.06)

fit3<-update(fit2,~.-BlackPathDam:WhiteFungLogis)
anova(fit3,fit2) #There is not a significant two way interaction 

fit4<-update(fit3,~.-BlackPathDam:ThripsDam)
anova(fit4,fit3)
#There is a significant interaction between black path dam and thrips dam. 

fit5<-update(fit3,~.-WhiteFungLogis:ThripsDam)
anova(fit5,fit3) #There is no interaction between these two. 

summary(fit5)

#is White path Damage significant alone? 
fit6<-update(fit5,~.-WhiteFungLogis)
anova(fit6,fit5) #White Fung logis is not important, although it has an identical AIC.   

summary(fit6)

fit7<-update(fit6,~.-BlackPathDam)
anova(fit7,fit6)

summary(fit7)

#The best model is one with thrips damage and and interaction between thrips and black pathogen damage. Oddly, the coefficent for thrips damage is positive, which seems like thrips damage increases performance, however this is likely just a reflection of there being more thrips damage and black pathogen damage on larger leaves, and of course plants with larger total leaf area will have larger leaves. Therefore, what i need to do is correct for leaf size when using pathogen data and have something like % infection on leaf. spots per leaf area? Otherwise, i am afraid that this model and all pathogen models are not informative. 

plot(ChlorA~GM_TotalLeaf_Area,data=dat2)
summary(lm(ChlorA~GM_TotalLeaf_Area,data=dat2))
#Interestinly, chlrophyllA is not associated with garlic mustard total leaf area -- our measure of performance. bizarre. Could this be because smaller leaves have much more chlorophyll? 

plot(ChlorA~GM_Leaf_Len,data=dat)
dat
#Not really no

MapleModel
dat2

```



#Modelling with infection per unit of area
```{r}
#Weighted pathogen damage data are no on too small of a scale. These will be standardized. 

MapleModel$ThripsDamW<-Standardize(MapleModel$ThripsDamW)
MapleModel$BlackPathDamW<-Standardize(MapleModel$BlackPathDamW)
MapleModel$WhiteFungDamW<-Standardize(MapleModel$WhiteFungDamW)


#Modelling random effects 
fit<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungLogis+(1|Family)+(1|gh_bench/gh_col),data=MapleModel)

fit2<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungLogis+(1|Family)+(1|gh_bench),data=MapleModel)

fit3<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungLogis+(1|gh_bench/gh_col),data=MapleModel)


#Is collumn important?
anova(fit,fit2) #Yes it is. 

#Is family important? 
anova(fit,fit3) #Yes family is very important, this is a different result from the one I received prior to weighing the pathogen data. 


#Modeling fixed effects: 

fit<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungLogis+(1|Family)+(1|gh_bench/gh_col),data=MapleModel)

fit2<-update(fit,~.-ThripsDamW:BlackPathDamW:WhiteFungLogis)
anova(fit,fit2) #Not a significant three way interaction.

fit3<-update(fit2,~.-BlackPathDamW:WhiteFungLogis)
anova(fit3,fit2) #There is not a significant two way interaction, although it is close (p=0.06)

fit4<-update(fit3,~.-BlackPathDamW:ThripsDamW)
anova(fit4,fit3)
#There is a significant interaction between black path dam and thrips dam. 

fit5<-update(fit3,~.-WhiteFungLogis:ThripsDamW)
anova(fit5,fit3) #There is no interaction between these two, although it is close

summary(fit5)

```



#Modelling with WhitPathDam Weighed, not logistic. -- Do not use this. not good science. 
```{r}
#Weighted pathogen damage data are no on too small of a scale. These will be standardized. 

#Modelling random effects 
fit<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungDamW+(1|Family)+(1|gh_bench/gh_col),data=MapleModel)

fit2<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungDamW+(1|Family)+(1|gh_bench),data=MapleModel)

fit3<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungDamW+(1|gh_bench/gh_col),data=MapleModel)


#Is collumn important?
anova(fit,fit2) #Yes it is. 

#Is family important? 
anova(fit,fit3) #Yes family is very important, this is a different result from the one I received prior to weighing the pathogen data. 


#Modeling fixed effects: 

fit<-lmer(GM_TotalLeaf_Area~Maple_TotalLeafArea_End+Fern+ThripsDamW*BlackPathDamW*WhiteFungDamW+(1|Family)+(1|gh_bench/gh_col),data=MapleModel)

fit2<-update(fit,~.-ThripsDamW:BlackPathDamW:WhiteFungDamW)
anova(fit,fit2) #Not a significant three way interaction.

fit3<-update(fit2,~.-BlackPathDamW:WhiteFungDamW)
anova(fit3,fit2) #There is not a significant two way interaction, 

fit4<-update(fit3,~.-BlackPathDamW:ThripsDamW)
anova(fit4,fit3)
#There is a significant interaction between black path dam and thrips dam. 

fit5<-update(fit3,~.-WhiteFungDamW:ThripsDamW)
anova(fit5,fit3) #There is a significant whitefung dam and thrips dam interaction. 

summary(fit3)
#These coeficients make much more sense, all in the negatives. Weighing was the appropriate thing to do. This should be done in models that predict pathogen response to glucosinolates and flavonoids. - Chlorophyll concentration should be used in those models as well. 
summary(fit3)
hist(residuals(fit3))
plot(residuals(fit3))
plot(fit3)


#In conclusion, Ferns, maple and all pathogens reduced garlic mustard performance in the maple treatment.

```







#Modelling: Negative Binomial- Fern abundance
```{r}
#Because there are two garlic mustard individuals per pot, and the unit we are looking at is only replicable at the pot level (fern abundance in a pot) duplicates within the same pot in the garlic mustard treatment need to be removed and averaged to remove pseudoreplication. 

#What i will do is make the competition number the tag for those in the GM treatment. This will have the effect of maintaining the leaf variation, but averaging it over each pot. 

# I will need to use dat2, summarized at the individual level, because we have a single observation at the pot level, not at the leaf level. 
datFern<-dat2
datFern$Tag<-as.character(datFern$Tag)
for(i in 1:length(datFern$Tag)){
  if(!is.na(datFern$comp_number[i])){
    datFern$Tag[i]<-datFern$comp_number[i]
  }
}
datFern
#I am excluding flavonoid concentration because there were no detectable flavonoids in the root samples. 

#Modelling random effects 
fit_full<-glmmTMB(Fern~treatment+gluc_Conc+ChlorA+(1|Family)+(1|gh_bench),family=nbinom2,data=datFern)

fit_full_0.1<-glmmTMB(Fern~treatment+gluc_Conc+ChlorA+(1|Family),family=nbinom2,data=datFern)

fit_full_0.2<-glmmTMB(Fern~treatment+gluc_Conc+ChlorA+(1|gh_bench),family=nbinom2,data=datFern)

anova(fit_full,fit_full_0.1)#Bench is an extremenly important predictor. 
anova(fit_full,fit_full_0.2)#Family is not. 


fit_full<-glmmTMB(Fern~treatment+gluc_Conc+ChlorA+(1|gh_bench),family=nbinom2,data=datFern[!is.na(datFern$gluc_Conc),])
fit_1<-glmmTMB(Fern~treatment+ChlorA+(1|gh_bench),family=nbinom2,data=datFern[!is.na(datFern$gluc_Conc),])
anova(fit_full,fit_1)#Glucosinolates are not a significant predictor of fern abundance (although the AIC is about the same)

summary(fit_full) #those with more ChlorA dont have less ferns. If anything, they have more ferns. 

fit_1<-glmmTMB(Fern~treatment+(1|gh_bench),family=nbinom2,data=datFern)
fit_2<-glmmTMB(Fern~1+(1|gh_bench),family=nbinom2,data=datFern)
anova(fit_2,fit_1)
#Fern abundance is predicted by treatment. 

summary(fit_1)$coef
plot(resid(fit_1))
plot(resid(fit_1)^2)

summary(fit_1)


#Permutation test
datPerTest<-datFern
zStoretreatGM<-c()
zStoretreatM<-c()

for(i in 1:500){
  #Randomize flavonoid concentration.
  datPerTest$treatment<-sample(datPerTest$treatment,length(datPerTest$treatment),replace = F)

  #New Model with randomized treatment and flavonoids
  newMod<-update(fit_1,data=datPerTest)
  
  # Extract test statistics for maple (M) and garlic mustard (gm) treatments
  MtreatZval<-summary(newMod)$coef[[1]][3,3]
  GMtreatZval<-summary(newMod)$coef[[1]][3,2]
  
  #Store z value.
  zStoretreatGM[i]<-GMtreatZval
  zStoretreatM[i]<-MtreatZval
}

sum(zStoretreatM>=2.316180)/length(zStoretreatM)
#Estimated p value for the maple treatment is 0.01. This is very close to the actual p value of 0.02
sum(zStoretreatGM>=2.231574)/length(zStoretreatGM)
#Estimated p value for the garlic mustard treatment is 0. This is close to the actual p value of 0.02

summary(fit_1)
```









