---
title: "Plasticity Analysis"
author: "Richard Honor"
date: "28/04/2020"
output: html_document
---

#Read in data. 
```{r}
library(ggplot2)
library(dplyr)
library(lmerTest)

#read in data
rm(list=ls())
dat<-read.csv("DataSynthesis.csv")

#Assign family column
prefamily<-gsub("*.\\|","",dat$Tag)
dat$Family<-gsub("\\-.*","",prefamily)

#remove those with fertilizer treatment, and extra genotypes that are only in the alone treatment. 
dat<-dat[!grepl("i",dat$Sample,fixed=T),]


#Creating leaf area vector 
dat$GM_Leaf_Area<-dat$GM_Leaf_Len*dat$GM_Leaf_Wid

sd(dat$GM_Leaf_Area,na.rm=T) # certain variables can affect the linear regression simply because of how large they are. I will standardize GM_Leaf_Area, which is clearly way too large. 

Standardize<-function(x){
  standard<-(x-mean(x,na.rm=T))/sd(x,na.rm=T)
}
dat$GM_Leaf_Area<-Standardize(dat$GM_Leaf_Area)


#Making WhiteFungalDamage Boolean 
dat$WhiteFungLogis<-NA
dat$WhiteFungLogis[dat$WhiteFungDam>0]<-"Yes"
dat$WhiteFungLogis[dat$WhiteFungDam==0]<-"No"


```

#Visualizing correlation between gluc, flav and chlorophyll. 
```{r}
source("GGPlot_Themes.R")
library(cowplot)
library(gridExtra)


dat$log1_flavConc<-log(dat$flav_Conc+1)
dat$log1_glucConc<-log(dat$gluc_Conc+1)
dat$log1_ChlorA<-log(dat$ChlorA+1)

dat$log_flavConc<-log(dat$flav_Conc)
dat$log_glucConc<-log(dat$gluc_Conc)
dat$log_ChlorA<-log(dat$ChlorA)


dat
flav<-ggplot(dat)+
  geom_point(aes(y=log1_flavConc,x=log1_ChlorA))+
  ylab(bquote(bold("[Flavonoid] Log("(mg/ml)~"+1)")))+
  xlab(bquote(bold("[Chlorophyll A] Log("(μg/ml)~"+1)")))+
  theme_simple_vert()


gluc<-ggplot(dat)+
  geom_point(aes(y=log1_glucConc,x=log1_ChlorA))+
  ylab(bquote(bold("[Glucosinolate] Log("(mg/ml)~"+1)")))+
  xlab(bquote(bold("[Chlorophyll A] Log("(mg/ml)~"+1)")))+
  theme_simple_vert()


tiff("Other_Figures/LogPlus1_GlucFlavChlor_Cor.tiff", units="in", width=12, height=6, res=300)
grid.arrange(gluc,flav,ncol=2)
dev.off()


flav<-ggplot(dat)+
  geom_point(aes(y=log_flavConc,x=log_ChlorA))+
  ylab(bquote(bold("[Flavonoid] Log("(mg/ml)~")")))+
  xlab(bquote(bold("[Chlorophyll A] Log("(μg/ml)~")")))+
  theme_simple_vert()


gluc<-ggplot(dat)+
  geom_point(aes(y=log_glucConc,x=log_ChlorA))+
  ylab(bquote(bold("[Glucosinolate] Log("(mg/ml)~")")))+
  xlab(bquote(bold("[Chlorophyll A] Log("(mg/ml)~")")))+
  theme_simple_vert()

tiff("Other_Figures/Log_GlucFlavChlor_Cor.tiff", units="in", width=12, height=6, res=300)
grid.arrange(gluc,flav,ncol=2)
dev.off()




dat %>% select(flav_Conc,gluc_Conc,log_flavConc,log_glucConc)

plot(flav_Conc~ChlorA,data=dat)
```





#Standardizing pathogen damage
Previous analysis have indicated that leaf size is a significant predictor of pathogen abudnance. This is because the larger the leaf, the more pathogens can be on the leaf. For this reason, I am weighing the Thrips damage and black pathogen damage by the leaf area, and then standardizing the variable. 
```{r}
Weigh<-function(x){
  x/(dat$GM_Leaf_Len*dat$GM_Leaf_Wid)
}

Standardize<-function(x){
  standard<-(x-mean(x,na.rm=T))/sd(x,na.rm=T)
}

#Weighing measurements by leaf area
dat$ThripsDamW<-Weigh(dat$ThripsDam)
dat$BlackPathDamW<-Weigh(dat$BlackPathDam)

#Standardizing measurements
dat$ThripsDamW<-Standardize(dat$ThripsDamW)
dat$BlackPathDamW<-Standardize(dat$BlackPathDamW)
dat$GM_Leaf_Area<-Standardize(dat$GM_Leaf_Area)

#Logging pathogen damage data variables as they are very skewed. 
dat$BlackPathDamW<-log(dat$BlackPathDamW+abs(min(dat$BlackPathDamW,na.rm=T)+1))
dat$ThripsDamW<-log(dat$ThripsDamW+abs(min(dat$ThripsDamW,na.rm=T)+1))


#Convering glucosinolate, flavonoid and chlorophyll, and fern to log scale. 
hist(dat$ChlorA)
hist(log(dat$ChlorA))
dat$ChlorA<-log(dat$ChlorA)

hist(dat$gluc_Conc)
hist(log(dat$gluc_Conc))
dat$gluc_Conc<-log(dat$gluc_Conc)


hist(dat$flav_Conc)
hist(log(dat$flav_Conc))
dat$flav_Conc<-log(dat$flav_Conc)

hist(dat$Fern)
hist(log(dat$Fern+1))
dat$Fern<-log(dat$Fern+1)



```


#What predicts glucosinolate concentration? (Apparent Plasticity)
```{r}
hist(dat$gluc_Conc) 
#The distribution looks faily normal, so i am going to use a linear mixed model. # My maximum model is one with possible interactions between pathogens, but no other interactions

#------------------
#Modelling Random Effects 

#Maximum model
fit<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat)

#Is Tag important?
fit2<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family)+(1|gh_bench),data=dat)
anova(fit,fit2)#The model with Tag is much better. 

#Is greenhouse bench important?
fit3<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag),data=dat)
anova(fit,fit3) #gh_Bench is very close to significant (p=0.051 i will keep it). 

#Is family important? (Genotype effects)
fit4<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Tag)+(1|gh_bench),data=dat)
anova(fit,fit4) #Family is very important.

#Is there a GXE interaction? 
fit5<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family:treatment)+(1|gh_bench),data=dat)
anova(fit2,fit5) #There is no GXE interaction

#------------------
#Modelling fixed effects. 

#Maximum model:
fit<-lmer(gluc_Conc~treatment+WhiteFungLogis*ThripsDamW*BlackPathDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat)

fit2<-update(fit,~.-WhiteFungLogis:ThripsDamW:BlackPathDamW)
anova(fit,fit2)

fit3<-update(fit2,~.-WhiteFungLogis:ThripsDamW)
anova(fit2,fit3)

fit4<-update(fit3,~.-ThripsDamW:BlackPathDamW)
anova(fit3,fit4)

fit5<-update(fit4,~.-WhiteFungLogis:BlackPathDamW)
anova(fit5,fit4)#There are no significant interactions. 


fit4<-lmer(gluc_Conc~treatment+BlackPathDamW+WhiteFungLogis+ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat)
summary(fit4) #White Fungi not important

#Removing WhiteFungLogis
fit4<-lmer(gluc_Conc~treatment+BlackPathDamW+ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat)
summary(fit4)#ThripsDam is not important

#Removing Fern
fit5<-lmer(gluc_Conc~treatment+BlackPathDamW+ThripsDamW+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat)
summary(fit5)##Fern is not important

#Removing BlackPathDam
fit6<-lmer(gluc_Conc~treatment+ThripsDamW+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat[!is.na(dat$BlackPathDamW),])
summary(fit6)

summary(fit6)#This is the best model. 
plot(fit6)#There still appears to be a pattern in the residuals, probably due to the skew in the data. 
qqnorm(residuals(fit6))
plot(residuals(fit6))

#Good fit.
confint(fit7,method="Wald")

```

#Visualization of treatment means
```{r}

Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(1.004860,1.004860-0.085363,1.004860-0.081203),upper=c(1.03596058,1.004860-0.05830764,1.004860-0.05602873),lower=c(0.973759648,1.004860-0.112418643,1.004860-0.106378092))

tiff("Plasticity_Figures/Apparent_Gluc-Treat.tiff", units="in", width=10, height=6, res=300)
ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Garlic Mustard","Maple"))+
  scale_y_continuous(limits = c(0.875,1.03), name = bquote(bold("[Glucosinolate] " (mg/mL))),breaks=c(0.875,0.9,0.925,0.95,0.975,1,1.025))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )
dev.off()
```


#What predicts glucosinolate concentration after controlling for resource allocation? (True Plasticity). 
```{r}
#Modelling Random Effects 

#Maximum model
fit<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+treatment:ChlorA+(1|Family/Tag)+(1|gh_bench),data=dat)

#Is Tag important?
fit2<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+treatment:ChlorA+(1|Family)+(1|gh_bench),data=dat)
anova(fit,fit2)#The model with Tag is better. 

#Is greenhouse bench important?
fit3<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+treatment:ChlorA+(1|Family/Tag),data=dat)
anova(fit,fit3) #greenhouse bench is not significant. I will remove it from the analysis. 

#Is family important? (Genotype effects)
fit4<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+treatment:ChlorA+(1|Tag)+(1|gh_bench),data=dat)
anova(fit,fit4) #Family is very important.

#Is there a GXE interaction? 
fit5<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+treatment:ChlorA+(1|Family:treatment)+(1|gh_bench),data=dat)
anova(fit2,fit5) #There is no GXE interaction


#Modelling Fixed Effects. 

#Maximum model
fit<-lmer(gluc_Conc~treatment+WhiteFungLogis*BlackPathDamW*ThripsDamW+Fern+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+treatment:ChlorA+(1|Family/Tag),data=dat)

fit1<-update(fit,~.- WhiteFungLogis:BlackPathDamW:ThripsDamW)
anova(fit,fit1) #No three way interaction

fit2<-update(fit1,~.- WhiteFungLogis:BlackPathDamW)
anova(fit2,fit1)#There is no significant interaction between White fungi presence and black pathogen damage. 

fit3<-update(fit2,~.- WhiteFungLogis:ThripsDamW)
anova(fit3,fit2) #No interaction

fit4<-update(fit3,~.- BlackPathDamW:ThripsDamW)
anova(fit4,fit3) #No interaction

summary(fit4) #Polynomial of leaf size isn't significant. 

fit5<-lmer(gluc_Conc~treatment+WhiteFungLogis+BlackPathDamW+ThripsDamW+Fern+GM_Leaf_Area+ChlorA+treatment:ChlorA+(1|Family/Tag),data=dat)
summary(fit5) #Fern not significant. (Although it is close p=0.08)

fit6<-lmer(gluc_Conc~treatment+WhiteFungLogis+BlackPathDamW+ThripsDamW+GM_Leaf_Area+ChlorA+treatment:ChlorA+(1|Family/Tag),data=dat)
summary(fit6) #Everything else is significant


#Is the interaction between ChlorA and treatment significant? 
fit9<-lmer(gluc_Conc~treatment+ThripsDamW+WhiteFungLogis+BlackPathDamW+GM_Leaf_Area+ChlorA+(1|Family/Tag),data=dat)
anova(fit9,fit6) #No, not with the logged data.  
summary(fit9)
#Black pathogen damage and white fungal damage are not significant. This is hte best model. 
#Is the interaction between ChlorA and treatment significant? 
fit10<-lmer(gluc_Conc~treatment+ThripsDamW+GM_Leaf_Area+ChlorA+(1|Family/Tag),data=dat)

plot(fit10)
summary(fit10)
qqnorm(residuals(fit10))
plot(residuals(fit10))
confint(fit10)

#The model is essentially the same as when chlorophyll A was not included. 

fit11<-lmer(gluc_Conc~treatment+ThripsDamW+GM_Leaf_Area+(1|Family/Tag),data=dat)
summary(fit11) #The effect of treatment is severyly reduced by including chlorophyll A, it was just so significant that the effect isnt completely masked. However, it can be considered to be the same with chlorophyll. 


```
Thrips damage, and treatment predict glucosinolate concentration after controlling for chlorophyll A, however, the lack of resources likely resulted in reduced production of glucosinolates before the reduced production of chlorophyll A - in other words, i think we are still observing apparent plasticity. Even the interaction between black pathogen damage and white fungal abundance is negative. 

I would not expect to observe a plastic responce of glucosinolates to thrips here because this is not a very good framework to test plasticity as we do not have replication of the same genotype without ferns. Therefore, there is no way to determine if it is plasticity we are seeing, in fact it is likely not because there is likely much more variation amoung individuals than within individuals ability to change. The fact that there is a negative correltion with thrips damage, suggests that there is less thrips damage at higher glucosinoalte concentration. 

#Visualization of treatment means # need to alter these estimates so that they represent the value when there is no pathogen damage. 
```{r}

Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(0.856937,0.856937-0.117213,0.856937-0.085803),upper=c(0.892913521,0.856937-0.073213020,0.856937-0.040556266),lower=c(0.820836302,0.856937-0.161217050,0.856937-0.131082248))

tiff("Plasticity_Figures/True_Gluc-Treat.tiff", units="in", width=10, height=6, res=300)
ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Garlic Mustard","Maple"))+
  scale_y_continuous(limits = c(0.7,0.925), name = bquote(bold("[Glucosinolate] " (mg/mL))),breaks=seq(0.7,0.925,0.025))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )
dev.off()
```



#What predicts flavonoid concentration? (Apparent Plasticity)
```{r}
hist(dat$flav_Conc) 
#The distribution looks faily normal, so i am going to use a linear mixed model. # My maximum model is one with possible interactions between pathogens, but no other interactions

#------------------
#Modelling Random Effects 

#Maximum model
fit<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag)+(1|gh_bench),data=dat)

#Is Tag important?
fit2<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family)+(1|gh_bench),data=dat)
anova(fit,fit2)#The model with Tag is not significant,although p=0.12, thereofer i will leave it in the model to avoid psuedoreplication

#Is greenhouse bench important?
fit3<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family/Tag),data=dat)
anova(fit,fit3) #gh_Bench is very significant. Keeping this in the analysis 

#Is family important? (Genotype effects)
fit4<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Tag)+(1|gh_bench),data=dat)
anova(fit,fit4) #Family is not important. 

#Is there a GXE interaction? 
fit5<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|Family:treatment)+(1|gh_bench),data=dat)
anova(fit2,fit5) #There is no GXE interaction

#Double check family is not important because there was no significant effect of Tag. 
fit6<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|gh_bench),data=dat)
anova(fit2,fit6) #Family is not important. 

#There is no significant family within family genetic variation for flavonoid concentration. 

#------------------
#Modelling fixed effects. 

#Maximum model:
fit<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+(1|gh_bench),data=dat)
summary(fit) #this is the best model, Does this change if we add in ChlorA to analyze active plasticity?
```

```{r}

#Active Plasticity
#Maximum model
fit<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|Family/Tag)+(1|gh_bench),data=dat)

#Is Tag important?
fit2<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|Family)+(1|gh_bench),data=dat)
anova(fit,fit2)#The model with Tag is not significant,although p=0.12, thereofer i will leave it in the model to avoid psuedoreplication

#Is greenhouse bench important?
fit3<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|Family/Tag),data=dat)
anova(fit,fit3) #gh_Bench is very significant. Keeping this in the analysis 

#Is family important? (Genotype effects)
fit4<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|Tag)+(1|gh_bench),data=dat)
anova(fit,fit4) #Family is not important. 

#Is there a GXE interaction? 
fit5<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|Family:treatment)+(1|gh_bench),data=dat)
anova(fit2,fit5) #There is no GXE interaction

#Double check family is not important because there was no significant effect of Tag. 
fit6<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|gh_bench),data=dat)
anova(fit2,fit6) #Family is not important. 


fit<-lmer(flav_Conc~treatment+GM_Leaf_Area+I(GM_Leaf_Area^2)+ChlorA+(1|gh_bench),data=dat)
summary(fit) #this is the best model, Does this change if we add in ChlorA to analyze active plasticity?

#There is again evidence that treatment is simply sharing the p value and effect with chlorophyll. Therefore, there is no evidence for active plasticity. 
```





#Visualization of treatment means # need to alter these estimates so that they represent the value when there is no pathogen damage. 
```{r}

fit5<-lmer(flav_Conc~treatment+WhiteFungLogis+ThripsDamW+Standardize(GM_Leaf_Area)+WhiteFungLogis:ThripsDamW+I(GM_Leaf_Area^2)+(1|gh_bench),data=dat)
summary(fit5)
confint(fit5)

Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(0.870911,0.870911-0.109820,0.870911-0.047032),upper=c(0.925244197,0.870911-0.075697392,0.870911-0.016697329),lower=c(0.809781689,0.870911-0.142820256,0.870911-0.077469660))

tiff("Plasticity_Figures/Apparent_Flav-Treat.tiff", units="in", width=10, height=6, res=300)
ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Garlic Mustard","Maple"))+
  scale_y_continuous(limits = c(0.7,0.925), name = bquote(bold("[Flavonoid] " (mg/mL))),breaks=seq(0.7,0.925,0.025))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )
dev.off()
```




Even after controlling for performance, the parameter for thips damagage is negative, suggesting that thrips reduce perforncance and allow for less resources to be allocated to flavonoids, even after controlling for the amount of thrips in the experiemnt. 

```{r}


fit7<-lmer(flav_Conc~treatment+ThripsDamW+Standardize(GM_Leaf_Area)+Standardize(ChlorA)+(1|gh_bench),data=dat)
summary(fit7)
confint(fit7)



Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(0.858419,0.858419-0.062538,0.858419+0.000828),upper=c(0.904711867,0.858419-0.031844088,0.858419+0.028342554),lower=c(0.80773760,0.858419-0.09248508,0.858419-0.02682881))

tiff("Plasticity_Figures/True_Flav-Treat.tiff", units="in", width=10, height=6, res=300)
ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Garlic Mustard","Maple"))+
  scale_y_continuous(limits = c(0.725,0.925), name = bquote(bold("[Flavonoid] " (mg/mL))),breaks=seq(0.725,0.925,0.025))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )
dev.off()
```



```{r}
#Generating plasticity estimate for Chlorophyll A 
fitCh<-lmer(ChlorA~treatment+GM_Leaf_Area+WhiteFungLogis:ThripsDamW+I(GM_Leaf_Area^2)+(1|gh_bench),data=dat)
summary(fitCh)
```
