---
title: "Plasticity_Analysis2.0"
author: "Richard Honor"
date: "04/06/2020"
output: html_document
---


#Read in and prep data
```{r}
library(ggplot2)
#library(lme4)
library(glmmTMB)
#library(tidyr)
library(cowplot)
library(grid)
library(gridExtra)
library(dplyr)
source("GGPlot_Themes.R")

#read in data
rm(list=ls())
dat<-read.csv("DataSynthesis.csv")

#Remove maple controls data from the data set.
dat<-dat %>% filter(treatment!="mcnt") %>% droplevels()

#remove those with fertilizer treatment, and extra genotypes that are only in the alone treatment. 
dat<-dat[!grepl("i",dat$Sample,fixed=T),]

#Initializing columns to avoid constant error messages. 
dat$WhiteFungLogis<-NA
dat$BlackFungLogis<-NA
```


#Generating data frames with summarized leaf data (dat2) and summarized genotype data (dat3)
```{r}
hist(dat$gluc_Conc)
hist(dat$flav_Conc)
#Both concentrations are above zero. 
min(dat$gluc_Conc,na.rm=T)
min(dat$flav_Conc,na.rm=T)


#Logging data
dat$Fern<-log(dat$Fern+1)
dat$gluc_Conc<-log(dat$gluc_Conc)
dat$flav_Conc<-log(dat$flav_Conc)
dat$ChlorA<-log(dat$ChlorA)
dat$ThripsDam<-log(dat$ThripsDam+1)
dat$BlackPathDam<-log(dat$BlackPathDam+1)
dat$Fern<-log(dat$Fern+1)



#Creating leaf area vector 
dat$GM_Leaf_Area<-dat$GM_Leaf_Len*dat$GM_Leaf_Wid


#Summarizing: Taking the mean value of leaves. This tibble contains data at the level of the plant means. 
dat2<-dat %>% group_by(Tag) %>% summarize(ChlorA=mean(ChlorA),ChlorB=mean(ChlorB),gluc_Conc=mean(gluc_Conc),flav_Conc=mean(flav_Conc),Family=first(Family),treatment=first(treatment),gh_row=first(gh_row),gh_bench=first(gh_bench),GM_TotalLeaf_Area=first(GM_TotalLeaf_Area),comp_number=first(comp_number),ThripsDam=mean(ThripsDam),WhiteFungDam=mean(WhiteFungDam),BlackPathDam=mean(BlackPathDam),Fern=mean(Fern),gh_col=first(gh_col),GM_Leaf_Area=mean(GM_Leaf_Area),Latitude=first(Latitude),Longitude=first(Longitude),Altitude=first(Altitude), RGR1=first(RGR1),GM_Leaf_Len_Initial=first(GM_Leaf_Len_Initial),
                                          GM_Fecundity=first(GM_Fecundity),
MapleFinalMass=first(MapleFinalMass),
GM_StemHeight_Bolt=first(GM_StemHeight_Bolt),
GM_Leaf_Number_Bolt=first(GM_Leaf_Number_Bolt),
Larg_Leaf_Len_Bolt=first(Larg_Leaf_Len_Bolt),
Larg_Leaf_Wid_Bolt=first(Larg_Leaf_Wid_Bolt),
Row_Field=first(Row_Field),
Maple_Died=first(Maple_Died))


#All of these genotypes died (15 Genotypes).(We are simply missing a final measurement for e|JBCHY1-1-50|Q|240) That is only 3% Mortality. 
dead<-dat2[is.na(dat2$GM_TotalLeaf_Area),]

#Removing those with dead competitors from the garlic mustard treatment. ("e|JBCHY1-1-50|Q|240") did not die, we are simply missing the final measurement for it.

dead_competitors<-dead %>% filter(treatment=="gm",Tag!="e|JBCHY1-1-50|Q|240") %>% select(comp_number)

#Removing those with dead competitors from the analysis. 
dat2<-dat2 %>% filter(!comp_number %in% dead_competitors$comp_number)
dat<-dat %>% filter(!comp_number %in% dead_competitors$comp_number)


##Summarizing: Taking the mean value of plants. This tibble contains data at the level of the family means within each treatment. 
#dat3<-dat2 %>% drop_na(GM_TotalLeaf_Area) %>% group_by(Family,treatment)  %>% summarize_if(is.numeric,mean)



#Because of how zero inflated white pathogen damage is, i will use a logistic regression to model it.
dat2$WhiteFungLogis<-NA
dat2$WhiteFungLogis[dat2$WhiteFungDam==0]<-0
dat2$WhiteFungLogis[dat2$WhiteFungDam>0]<-1


  #Function to standardize variables. 
Standardize<-function(x){
  standard<-(x-mean(x,na.rm=T))/sd(x,na.rm=T)
}

#Standardizing leaf area. 
dat2$GM_Leaf_Area<-Standardize(dat2$GM_Leaf_Area)

#Function to extract random effect heritabilities from a glmmTMB model. 
Xtract<-function(x,Resi){
  temp<-VarCorr(x)
GXE=temp$cond$`Family:treatment`[[1]]
E=temp$cond$treatment[[1]]
G=temp$cond$Family[[1]]

G_by_E<-GXE/(GXE+E+G+Resi)
Envir<-E/(GXE+E+G+Resi)
Genet<-G/(GXE+E+G+Resi)
data.frame(Type=c("GXE","E","G"),Value=c(G_by_E,Envir,Genet)*100)
}

#Function to extract residuals from models. 
resiCalc<-function(formula, ...){
  
  #Extracting residuals
fit<-lm(formula, ...)

Residual<-as.data.frame(resid(fit))

resi<-tibble::rownames_to_column(Residual, "Pos")

#Extracting the length of the data frame. 
resi[,1]<-as.numeric(resi[,1])
a<-max(resi[,1])

#Adding in NA values where there are none. ...

#Creating NA data frame 
blankDF<-data.frame(Pos=seq(1:a),blank=NA)
#Joining NA data frame to create new rows with NA where data is missing. 
newDF<-left_join(blankDF,resi,by="Pos") %>% select(-blank)

return(Standardize(newDF[,2]))
}



#Creating Survival Data.1 = survived, 0= dead.
dat2$Bolt_Survival<-c()
dat2$Bolt_Survival[dat2$GM_StemHeight_Bolt=="Dead"]<-0
dat2$Bolt_Survival[dat2$GM_StemHeight_Bolt!="Dead"]<-1

#Changing those i thought had died to alive. 
dat2$Bolt_Survival[dat2$GM_StemHeight_Bolt=="Dead"&!is.na(dat2$GM_Fecundity)]<-1


#Creating Maple Survival Data.1 = survived, 0= dead.
dat2$Maple_Survival<-c()
dat2$Maple_Died<-as.character(dat2$Maple_Died)
dat2$Maple_Survival[dat2$Maple_Died!="Y"]<-1
dat2$Maple_Survival[dat2$Maple_Died=="Y"]<-0
dat2<-dat2 %>% select(-Maple_Died)
```


#Pca of glucosinolate and chlorophyll 
```{r}
#Running PCA
pcaGlucCor<-prcomp(~Standardize(ChlorA)+Standardize(gluc_Conc),data=dat2,na.action=na.omit)
biplot(pcaGlucCor)
pcaGlucCor
summary(pcaGlucCor)

#Loading to data frame.
prediction<-as.data.frame(predict(pcaGlucCor))

#addings PCs to the data frame. 
df2<-tibble::rownames_to_column(prediction, "rownumber")
dat2[df2$rownumber,"PCCG_1"]<-df2$PC1
dat2[df2$rownumber,"PCCG_2"]<-df2$PC2

hist(dat2$PCCG_1)
```


#Generating PCA for Glucosinolate, Flavonoid and Chlorophyll
```{r}
#######
#Trying a pca with all three variables.
#########
pcaGlucCorFlav<-prcomp(~Standardize(gluc_Conc)+Standardize(ChlorA)+Standardize(flav_Conc),data=dat2,na.action=na.omit)
biplot(pcaGlucCorFlav)
pcaGlucCorFlav
summary(pcaGlucCorFlav)
pcaGlucCorFlav
#Loading to data frame.
prediction<-as.data.frame(predict(pcaGlucCorFlav))


df2<-tibble::rownames_to_column(prediction, "rownumber")
dat2[df2$rownumber,"PC1AllCGF"]<-df2$PC1
dat2[df2$rownumber,"PC2All_CF"]<-df2$PC2
dat2[df2$rownumber,"PC3All_CG"]<-df2$PC3

#PC2 is off diagonal for flav. (Higher values is higher flavonoid:Chlorophyll)
#PC3 is the off diagonal for glucosinolate.  (Higher values is higher glucosinolate:Chlorophyll)



```




#PCA of GM SIZE in the second year. 
```{r}
#Removing dead individuals with zeros. 
dat2$GM_StemHeight_Bolt[which(dat2$GM_StemHeight_Bolt=="Dead")]<-0
dat2$GM_Leaf_Number_Bolt[which(dat2$GM_Leaf_Number_Bolt=="Dead")]<-0
dat2$Larg_Leaf_Len_Bolt[which(dat2$Larg_Leaf_Len_Bolt=="Dead")]<-0
dat2$Larg_Leaf_Wid_Bolt[which(dat2$Larg_Leaf_Wid_Bolt=="Dead")]<-0

#Making data numeric
dat2$GM_StemHeight_Bolt<-as.numeric(dat2$GM_StemHeight_Bolt)
dat2$GM_Leaf_Number_Bolt<-as.numeric(dat2$GM_Leaf_Number_Bolt)
dat2$Larg_Leaf_Len_Bolt<-as.numeric(dat2$Larg_Leaf_Len_Bolt)
dat2$Larg_Leaf_Wid_Bolt<-as.numeric(dat2$Larg_Leaf_Wid_Bolt)


pca<-prcomp(~GM_StemHeight_Bolt+GM_Leaf_Number_Bolt+Larg_Leaf_Len_Bolt+Larg_Leaf_Wid_Bolt,data=dat2,scale.=T,na.action=na.omit)
summary(pca)
pca

prediction<-as.data.frame(predict(pca))

df<-tibble::rownames_to_column(prediction, "rownumber")

dat2[df$rownumber,"PC1BoltSize"]<-df$PC1

hist(dat2$PC1BoltSize) #The data is very zero inflated because of the mortality. This isnt great but what can you do. 
```


#I dont think another pca is the way to go. 

pcaAll<-prcomp(~Standardize(gluc_Conc)+Standardize(ChlorA)+(Standardize(RGR1)+Standardize(GM_TotalLeaf_Area)+Standardize(flav_Conc)),data=dat2,na.action=na.omit)
summary(pcaAll)
biplot(pcaAll)
pcaAll


#Fitness and bolt size variance partition analysis 
```{r}
#Fecundity
fit<-glmmTMB(GM_Fecundity~1+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(GM_Fecundity~1+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(GM_Fecundity~1+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(GM_Fecundity~1+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,5.611e+00) #Large effect of treatment on the values fecundity. 


#Survival 
#some genotypes that were recorded as dead actually grew again from the root to produce a bolt and seeds. I am replacing these with a 1 to designate that they are alive. 


#Conducting analysis on Survival
fit<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|treatment/Family)+(1|Family),data=dat2,family="binomial")
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|treatment)+(1|Family),data=dat2,family="binomial")
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|treatment),data=dat2,family="binomial")
anova(fit2,fit3)#Yes, very strong effect. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|Family),data=dat2,family="binomial")
anova(fit2,fit4)#No, Not at all. 

summary(fit)
Xtract(fit,pi^2/3) #Large effect of treatment on the values fecundity. 
df.residual(fit)
pi^2/3


#Bolt Size

#Is there an effect of row? 
fit0.1<-glmmTMB(PC1BoltSize~1+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
fit<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|treatment/Family)+(1|Family),data=dat2)
anova(fit,fit0.1) #Yes there is

#Is there an effect of GXE? 
fit2<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes 

#Is there an effect of treatment? 
fit4<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,3.163e+00 ) 


```


#Glucosinolate genetic variation..... 
```{r}
#Raw value test
fit<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(gluc_Conc~GM_Leaf_Area+(1|gh_bench),data=dat2)
anova(fit,fit2) #Some significance

#PCA Test
fit<-glmmTMB(PCCG_2~as.factor(Family),data=dat2)
fit2<-glmmTMB(PCCG_2~1,data=dat2)
anova(fit,fit2) #Much more significance. 

#GH_Bench not significant. 
fit<-glmmTMB(PCCG_2~as.factor(Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(PCCG_2~as.factor(Family),data=dat2)
anova(fit,fit2) 


#Creating data frame for plotting.

#Inserting family column into data frame.
newframe<-dat2[!is.na(dat2$PCCG_2)&!is.na(dat2$Family),] %>% select(Family)

#Obtaining population means and standard errors around those means, and sample size
newframe$Estimate<-predict(fit,se.fit=T)$fit
newframe$SE<-predict(fit,se.fit=T)$se.fit
newframe$N<-newframe$Family#Adding in extra family column under the name of N because this column will be used to obtain sample size and the original family collumn will be used to give an ID. 

#summarizing the data and obtaining the sample size for each estimate.
newframe2<-newframe %>% group_by(Family) %>%  summarize(Family=first(Family),N=n(),Estimate=mean(Estimate),SE=mean(SE))

#Adding in confidence intervals
newframe2$Lower<-qt(0.025,newframe2$N-1)*newframe2$SE
newframe2$Upper<-qt(0.975,newframe2$N-1)*newframe2$SE

source("GGPlot_Themes.R")

p<-ggplot(newframe2)+
  geom_point(aes(y=Estimate,x=Family,shape=Family))+
  geom_linerange(aes(ymin=Lower+Estimate,ymax=Upper+Estimate,x=Family,colour=Family))+
  ylab("Relative Glucosinolate Investment")+
  scale_y_continuous(breaks=seq(-1,2,0.1))+
   scale_shape_manual(values=c(0,1,2,3,4,5,7,8,9,11,12,0,1,2,3,4,5,7,8,9,11,12,4))+
  theme_simple( )%+replace%     
  theme(axis.title.y =  element_text(color = "black", size = 12, angle=90,vjust= 0.5,margin=margin(0,5,0,0)),
      axis.title.x =  element_text(color = "black", size = 12,margin=margin(5,0,0,0)),
            legend.text = element_text(color = "black", size = 10 ),
            axis.text.x = element_text(color = "black", size = 8),
      axis.text.y = element_text(color = "black", size = 10)
)


tiff("Plasticity_Figures/RGI_Investment(PCA_W_Gluc_Chlor_Only).tiff", units="in", width=14, height=8, res=300)
p
dev.off


```


#Gluc Flav variance partition analysis
```{r}
#Glucosinolate
fit<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. 

#Is there an effect of treatment? 
fit4<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,0.067131)



##Flavonoids...
fit<-glmmTMB(flav_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(flav_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(flav_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(flav_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,7.751e-02)


```

#Total leaf area RGR and Chlor A
```{r}
#looking at effect with and without black path dam
#Total leaf area. 
fit<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)

#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,0.5898)


#Looking at effect with black path dam.

#Total leaf area. 
fit<-glmmTMB(Standardize(GM_TotalLeaf_Area)~Standardize(BlackPathDam)+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)

#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(GM_TotalLeaf_Area)~Standardize(BlackPathDam)+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(GM_TotalLeaf_Area)~Standardize(BlackPathDam)+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(GM_TotalLeaf_Area)~Standardize(BlackPathDam)+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,0.39888)

dat2$GM_Leaf_Len_Initial

##Relative growth rate. 
fit<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,5.626e-01)

##Chlor A
fit<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,8.592e-01)



```




#Principle component glucosinolate, chlorophyll, flavonoid
```{r}
#########
#PC1
#########
fit<-glmmTMB(PC1AllCGF~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(PC1AllCGF~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2) #No.

#Is there an effect of family? 
fit3<-glmmTMB(PC1AllCGF~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
summary(fit3)
anova(fit2,fit3)#No... not when assessing in this model. 

#Is there an effect of treatment? 
fit4<-glmmTMB(PC1AllCGF~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes, very strong. 

summary(fit)
Xtract(fit,1.874) #Extremely high environmental effect fot PC1

#######
#PC2 This is the flavonoid off diagonal. 
#########
fit<-glmmTMB(PC2All_CF~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(PC2All_CF~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(PC2All_CF~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(PC2All_CF~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)# Yes, there is an effect of treatment. This is... interesting. 

Xtract(fit, 0.414090) #Extremely high Genetic effect for PC2
#Very interesting. 

#########
#PC3 glucosinolate off diagonal. 
#########
fit<-glmmTMB(PC3All_CG~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(PC3All_CG~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(PC3All_CG~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. Still highly significant effect of family. 

#Is there an effect of treatment? 
fit4<-glmmTMB(PC3All_CG~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)# No, no effect of treatment at all. 

summary(fit)
Xtract(fit,2.453e-01) #Extremely high Genetic effect for PC2
#Very interesting. 

```



#PC1 and PC2 treatment as a fixed effect... 
```{r}
library(glmmTMB)
#PC1AllCGF
#Maximum model
fit<-glmmTMB(PC1AllCGF~treatment+GM_Leaf_Area+(1|Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(PC1AllCGF~treatment+GM_Leaf_Area+(1|Family),data=dat2)
fit3<-glmmTMB(PC1AllCGF~treatment+GM_Leaf_Area+(1|gh_bench),data=dat2)
fit3.3<-glmmTMB(PC1AllCGF~treatment+GM_Leaf_Area+(1|Family/treatment),data=dat2)

anova(fit2,fit3.3) #Is a GXE significant? # no. 
anova(fit,fit2) #Greenhouse bench is not
anova(fit3,fit) #Family is not  

#Significance of plasticity for glucosinolates 
fit<-glmmTMB(PC1AllCGF~treatment+Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
fit4<-glmmTMB(PC1AllCGF~Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
anova(fit,fit4)#Highly significant. 
summary(fit)
confint(fit)

#Interestingly garlic mustard and maple treatment reduced PC1 by approximately the same ammount. 


#PC2All_CF
fit<-glmmTMB(PC2All_CF~treatment+GM_Leaf_Area+(1|Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(PC2All_CF~treatment+GM_Leaf_Area+(1|Family),data=dat2)
fit3<-glmmTMB(PC2All_CF~treatment+GM_Leaf_Area+(1|gh_bench),data=dat2)
fit3.3<-glmmTMB(PC2All_CF~treatment+GM_Leaf_Area+(1|Family/treatment),data=dat2)

anova(fit2,fit3.3) #Is a GXE significant? # no. 
anova(fit,fit2) #Greenhouse bench is.
anova(fit3,fit) #Family is not  

#Significance of plasticity for RFI 
fit<-glmmTMB(PC2All_CF~treatment+Standardize(GM_Leaf_Area)+(1|gh_bench),data=dat2)
fit4<-glmmTMB(PC2All_CF~Standardize(GM_Leaf_Area)+(1|gh_bench),data=dat2)
anova(fit,fit4)#very significant. 
summary(fit)
confint(fit)
#Interestingly, PC2... with flavonoids increased quite a bit in the maple treatment. .. This means the maple treatment has a higher flavonoid :Chlorophyll ratio. 

#PC3All_CG
fit<-glmmTMB(PC3All_CG~treatment+GM_Leaf_Area+(1|Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(PC3All_CG~treatment+GM_Leaf_Area+(1|Family),data=dat2)
fit3<-glmmTMB(PC3All_CG~treatment+GM_Leaf_Area+(1|gh_bench),data=dat2)
fit3.3<-glmmTMB(PC3All_CG~treatment+GM_Leaf_Area+(1|Family/treatment),data=dat2)

anova(fit2,fit3.3) #Is a GXE significant? # no. 
anova(fit,fit2) #Greenhouse bench is not.
anova(fit3,fit) #Family is   

#Significance of plasticity for glucosinolates 
fit<-glmmTMB(PC3All_CG~treatment+Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
fit4<-glmmTMB(PC3All_CG~Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
anova(fit,fit4)#Not significant. 
summary(fit)
confint(fit)


```

#Visualization of PC1 and PC2 treatment means glucosinolate
```{r}
source("GGPlot_Themes.R")

fit<-glmmTMB(PC1AllCGF~treatment+Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
summary(fit)
confint(fit)

#Visualizing PC1 plasticity
a<- 0.63831
gm<-0.63831-0.96451 
m<-0.63831-0.95331
Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(a,gm,m),upper=c(0.9058242,a-0.5619433,a-0.5961106),lower=c(0.37080059,a-1.36708561,a-1.31051768 ))

Vis
PC1<-ggplot(Vis)+
  geom_pointrange(aes(x = treatment, y = estimate,ymin=lower,ymax=upper, colour = treatment),size = 1)+
  scale_x_discrete(name="",labels=c("Alone","Intraspecific","Interspecific"))+
  scale_y_continuous(expand = c(0.25,0), name = "Leaf Quality (PC1)",breaks=seq(-1,1.5,0.25))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )

```
#PC2_CF Visualiztion
```{r}
source("GGPlot_Themes.R")

fit<-glmmTMB(PC2All_CF~treatment+Standardize(GM_Leaf_Area)+(1|gh_bench),data=dat2)
summary(fit)
confint(fit)

#Visualizing PC1 plasticity
a<- -0.10006
gm<--0.10006-0.12847 
m<--0.10006+0.20162
Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(a,gm,m),upper=c(0.1613922,a+0.0642846,a+0.3705575),lower=c(-0.36150847 ,a-0.32122553 ,a+0.03268481 ))


PC2<-ggplot(Vis)+
  geom_pointrange(aes(x = treatment, y = estimate,ymin=lower,ymax=upper, colour = treatment),size = 1)+
  scale_x_discrete(name="",labels=c("Alone","Intraspecific","Interspecific"))+
  scale_y_continuous(expand = c(0.25,0), name = "Relative Flavonoid Investment (PC2)",breaks=seq(-1,1.5,0.15))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )


tiff("Plasticity_Figures/PC1andPC2Plasticity.tiff", units="in", width=12, height=6, res=300)
plot_grid(PC1,PC2,labels = c("a","b"),rel_widths = c(1.1,1),label_size=18)
dev.off()

```
```


#Glucosinolate plastsicity
```{r}
library(glmmTMB)
#Maximum model
fit<-glmmTMB(gluc_Conc~treatment+GM_Leaf_Area+(1|Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(gluc_Conc~treatment+GM_Leaf_Area+(1|Family),data=dat2)
fit3<-glmmTMB(gluc_Conc~treatment+GM_Leaf_Area+(1|gh_bench),data=dat2)
fit3.3<-glmmTMB(gluc_Conc~treatment+GM_Leaf_Area+(1|Family/treatment),data=dat2)

anova(fit2,fit3.3) #Is a GXE significant? # no. 
anova(fit,fit2) #Greenhouse bench is not
anova(fit3,fit) #Family and Tag is very significant. 

#Significance of plasticity for glucosinolates 
fit<-glmmTMB(gluc_Conc~treatment+Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
fit4<-glmmTMB(gluc_Conc~Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
anova(fit,fit4)
summary(fit)
confint(fit)

#"Active plasticity" Eventhough it could still be passive after accounting for chlorophyll
fit<-glmmTMB(gluc_Conc~treatment+Standardize(GM_Leaf_Area)+Standardize(ChlorA)+(1|Family),data=dat2)
fit2<-glmmTMB(gluc_Conc~Standardize(GM_Leaf_Area)+Standardize(ChlorA)+(1|Family),data=dat2)
anova(fit,fit2)
confint(fit)

summary(fit) #Treatment is still significant, however, the magnitude of the significance is much reduced, i think that it is sharing the significance with chlorophyll. 
```

#Visualization of Apparent treatment means glucosinolate
```{r}
source("GGPlot_Themes.R")

#Visualizing passive plasticity
a<--1.55899177
gm<--1.55899177-0.16618664
m<--1.55899177-0.18518751
Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(a,gm,m),upper=c(-1.50051001,a-0.09022637,a-0.11887264),lower=c(-1.61747353,a-0.24214691,a-0.25150238 ))


Gpassive<-ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Intraspecific","Interspecific"))+
  scale_y_continuous(limits = c(-1.9,-1.4), name = bquote(bold("[Glucosinolate] (log" (mg/mL)~")")),breaks=seq(-1.9,-1.4,by=0.1))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )

a<--1.63713694
gm<--1.63713694-0.06113577
m<--1.63713694-0.07089345
Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(a,gm,m),upper=c(-1.585805632,a-0.005747620,a-0.021957509),lower=c(-1.68846825,a-0.11652391,a-0.11982939 ))

#Visualizing Active plasticity
Gactive<-ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Intraspecific","Interspecific"))+
  scale_y_continuous(limits = c(-1.9,-1.4),breaks=seq(-1.9,-1.4,by=0.1))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()

tiff("Plasticity_Figures/Glucosinolate_Plasticity.tiff", units="in", width=12, height=6, res=300)
plot_grid(passive,active,labels = c("a","b"),rel_widths = c(1.1,1))
dev.off()
```

#Flavonoid plasticity
```{r}
library(glmmTMB)
#Maximum model
#Convergence problem forced to use replication at family level, not individual level
fit<-glmmTMB(flav_Conc~treatment+Standardize(GM_Leaf_Area)+(1|Family)+(1|gh_bench),data=dat2)
fit2<-glmmTMB(flav_Conc~treatment+Standardize(GM_Leaf_Area)+(1|Family),data=dat2) 
fit3<-glmmTMB(flav_Conc~treatment+Standardize(GM_Leaf_Area)+(1|gh_bench),data=dat2) #Convergence problem

fit3.3<-glmmTMB(flav_Conc~treatment+Standardize(GM_Leaf_Area)+(1|Family/treatment),data=dat2) 

anova(fit2,fit3.3)#No GXE effect. 
anova(fit,fit2) #Greenhouse bench is significant

anova(fit3,fit) #Family is not significant at all. No genetic variation for family.

summary(fit3)
confint(fit3)


#"apparent plasticity" Eventhough it could still be passive after accounting for chlorophyll
fit<-glmmTMB(flav_Conc~treatment+Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
fit2<-glmmTMB(flav_Conc~Standardize(GM_Leaf_Area)+(1|Family),data=dat2)
summary(fit2)

anova(fit,fit2)




#"Active plasticity" Eventhough it could still be passive after accounting for chlorophyll
fit<-glmmTMB(flav_Conc~treatment+Standardize(GM_Leaf_Area)+Standardize(ChlorA)+(1|Family),data=dat2)

fit2<-glmmTMB(flav_Conc~Standardize(GM_Leaf_Area)+Standardize(ChlorA)+(1|Family),data=dat2)
summary(fit2)

anova(fit,fit2) #Treatment is not significant with flavonoids after accounting for chlorophyll. 
summary(fit)
confint(fit)

```

#Visualization of treatment means flavonoid
```{r}
#Visualizing passive plasticity
a<--2.21675805
gm<--2.21675805-0.20969999
m<--2.21675805-0.10422161
Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(a,gm,m),upper=c(-2.11846559,a-0.12720992,a-0.03237505),lower=c(-2.31505050,a-0.29219007,a-0.17606816 ))


Fpassive<-ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Intraspecific","Interspecific"))+
  scale_y_continuous(limits = c(-2.6,-2), name = bquote(bold("[Flavonoid] (log" (mg/mL)~")")),breaks=seq(-2.6,-2,by=0.1))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()+theme(
    axis.title.y =  element_text(color = "black", size = 16, face = "bold",margin=margin(3,20,3,0),angle = 90),
  )



#Visualizing active plasticity
a<--2.26994454
gm<--2.26994454-0.08570059
m<--2.26994454-0.01716435
Vis<-data.frame(
  treatment=c("Alone","Garlic Mustard","Maple"),estimate=c(a,gm,m),upper=c(-2.2211349151,a-0.0123743864,a+0.0487751134),lower=c(-2.3187541572,a-0.1590268033,a-0.0831038233 ))


Factive<-ggplot(Vis,aes(x = treatment, 
                    y = estimate, colour = treatment))+
  geom_point(size = 5)+
  geom_errorbar(ymin = Vis$lower,
                ymax = Vis$upper, width = 0.1)+
  scale_x_discrete(name="",labels=c("Alone","Intraspecific","Interspecific"))+
  scale_y_continuous(limits = c(-2.6,-2), name = bquote(bold("[Flavonoid] (log" (mg/mL)~")")),breaks=seq(-2.6,-2,by=0.1))+
  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Garlic Mustard","Maple"))+
  theme_simple_multiCol()

tiff("Plasticity_Figures/Flavonoid_Plasticity.tiff", units="in", width=12, height=6, res=300)
plot_grid(Fpassive,Factive,labels = c("a","b"),rel_widths = c(1.1,1))
dev.off

```

#four panel plot
```{r}

tiff("Plasticity_Figures/FlavGluc_Plasticity.tiff", units="in", width=12, height=10, res=300)

plot_grid(Gpassive,Gactive,Fpassive,Factive,labels = c("a","b","c","d"),align = "hv",label_fontfamily = "Arial",label_size = 18)

dev.off()

```













#Visualizing correlation between gluc, flav and chlorophyll. 
```{r}
source("GGPlot_Themes.R")
library(cowplot)
library(gridExtra)




flav<-ggplot(dat)+
  geom_point(aes(y=flav_Conc,x=ChlorA))+
  ylab(bquote(bold("[Flavonoid] (log"*(mg/ml)*")")))+
  xlab(bquote(bold("[Chlorophyll A] (log"*(μg/ml)*")")))+
  geom_abline(slope=0.3939,intercept = -1.8336,size=1)+
  scale_y_continuous(breaks = seq(-4,1,0.25))+
  scale_x_continuous(breaks = seq(-4,1,0.5))+
  theme_simple_vert()
flav

gluc<-ggplot(dat)+
  geom_point(aes(y=gluc_Conc,x=ChlorA))+
  ylab(bquote(bold("[Glucosinolate] (log"*(mg/ml)*")")))+
  xlab(bquote(bold("[Chlorophyll A] (log"*(μg/ml)*")")))+
    geom_abline(slope=0.45340,intercept = -1.14540,size=1 )+
   scale_y_continuous(breaks = seq(-4,0,0.25))+
  scale_x_continuous(breaks = seq(-4,1,0.5))+
  theme_simple_vert()
gluc

flavfit<-lm(flav_Conc~ChlorA,data=dat)
glucfit<-lm(gluc_Conc~ChlorA,data=dat)

flavglucfit<-lm(gluc_Conc~flav_Conc,data=dat)

summary(flavfit)
summary(glucfit)
summary(flavglucfit)

tiff("Other_Figures/Log_GlucFlavChlor_Cor.tiff", units="in", width=12, height=6, res=300)
plot_grid(gluc,flav,ncol=2,nrow=1,labels=c("a","b"),label_fontfamily = "Arial",label_size = 18)
dev.off()


```



