---
title: "Publication_Analysis_2"
output: html_document
---

#Read in and prep data
```{r}
library(ggplot2)
library(glmmTMB)
library(cowplot)
library(grid)
library(gridExtra)
library(dplyr)
source("GGPlot_Themes.R")

#read in data
rm(list=ls())
dat<-read.csv("DataSynthesis.csv")


#remove those with fertilizer treatment, and extra genotypes that are only in the alone treatment. 
dat<-dat[!grepl("i",dat$ID,fixed=T),]


#Initializing columns to avoid constant error messages. 
dat$WhiteFungLogis<-NA
dat$BlackFungLogis<-NA

#Function to standardize variables. 
Standardize<-function(x,meanSTD=F){
  if(meanSTD==T){
    
        standard<-(x/mean(x,na.rm=T))

  }
  else{  standard<-(x-mean(x,na.rm=T))/sd(x,na.rm=T) }


  return(standard)
}



```


#Generating data frames with summarized leaf data (dat2) and summarized genotype data (dat3)
```{r}

 #Logging data
  dat$Fern<-log(dat$Fern+1)
  dat$gluc_Conc<-log(dat$gluc_Conc)
  dat$flav_Conc<-log(dat$flav_Conc)
  dat$ChlorA<-log(dat$ChlorA)
 dat$ThripsDam<-log(dat$ThripsDam+1)
dat$BlackPathDam<-log(dat$BlackPathDam+1)

#Creating leaf area vector 
dat$GM_Leaf_Area<-dat$GM_Leaf_Len*dat$GM_Leaf_Wid

#Summarizing: Taking the mean value of leaves. This tibble contains data at the level of the plant means. 
dat2<-dat %>% group_by(Tag) %>% summarize(ChlorA=mean(ChlorA),ChlorB=mean(ChlorB),gluc_Conc=mean(gluc_Conc),flav_Conc=mean(flav_Conc),Family=first(Family),treatment=first(treatment),gh_row=first(gh_row),gh_bench=first(gh_bench),GM_TotalLeaf_Area=first(GM_TotalLeaf_Area),comp_number=first(comp_number),ThripsDam=mean(ThripsDam),WhiteFungDam=mean(WhiteFungDam),BlackPathDam=mean(BlackPathDam),Fern=mean(Fern),gh_col=first(gh_col),GM_Leaf_Area=mean(GM_Leaf_Area),Latitude=first(Latitude),Longitude=first(Longitude),Altitude=first(Altitude),
GM_StemHeight_Bolt=first(GM_StemHeight_Bolt),
GM_Leaf_Number_Bolt=first(GM_Leaf_Number_Bolt),
Larg_Leaf_Len_Bolt=first(Larg_Leaf_Len_Bolt),
Larg_Leaf_Wid_Bolt=first(Larg_Leaf_Wid_Bolt),
Row_Field=first(Row_Field),
Col_Field=first(Col_Field),
Maple_Died=first(Maple_Died),
Maple_TotalLeafArea_End=first(Maple_TotalLeafArea_End),
GM_Fecundity=first(GM_Fecundity),
MapleFinalMass=first(MapleFinalMass),
RGR1=first(RGR1),
NumberOfSamples=n(),
maple_height_0=first(maple_height_0),
maple_leaf_length_0=first(maple_leaf_length_0),
maple_leaves_0=first(maple_leaves_0),
Maple_StemHeight_End=first(Maple_StemHeight_End),
Maple_LeafNum_End=first(Maple_LeafNum_End),
Maple_TotalLeafArea_End=first(Maple_TotalLeafArea_End),
MapleDamage=mean(Maple_Damage_End)
)

#All of these genotypes died (15 Genotypes).(We are simply missing a final measurement for e|JBCHY1-1-50|Q|240) That is only 3% Mortality. 
dead<-dat2[is.na(dat2$GM_TotalLeaf_Area),]

deadID<-dead %>% filter(treatment!="mcnt",Tag!="e|JBCHY1-1-50|Q|240") #Here there are 12 putative dead competitors because  ("e|JBCHY1-1-50|Q|240") did not die. 

#Creating a collumn for those that survived (1) or died (2) in the greenhouse
dat2$GreenhouseSurvival<-c()
dat2$GreenhouseSurvival[dat2$Tag %in% deadID$Tag]<-0
dat2$GreenhouseSurvival[is.na(dat2$GreenhouseSurvival)]<-1


#Creating a column to model white pathogen presence (1= present on leaf)
dat2$WhiteFungLogis<-NA
dat2$WhiteFungLogis[dat2$WhiteFungDam==0]<-0
dat2$WhiteFungLogis[dat2$WhiteFungDam>0]<-1
dat2$WhiteFungLogis<-as.factor(dat2$WhiteFungLogis)


#Creating column to indivate whether bolts survived in the field or not (1 = survived, 0 = died).
dat2$Bolt_Survival<-c()
dat2$Bolt_Survival[dat2$GM_StemHeight_Bolt=="Dead"]<-0
dat2$Bolt_Survival[dat2$GM_StemHeight_Bolt!="Dead"]<-1
dat2$Bolt_Survival[is.na(dat2$GM_StemHeight_Bolt)]<-0 # I am going to be consistent and call those without a value dead because i missed these ones. 
dat2$Bolt_Survival[dat2$GM_Fecundity>0]<-1 #Those with fecundity data are also alive... 
dat2$Bolt_Survival[dat2$treatment=="mcnt"]<-NA #those that dies in year 1 are NA
dat2$Bolt_Survival[dat2$treatment=="mcnt"]<-NA #Maple controls are NA


#Creating a column to indicate wheter maples survived in year 2 or not.
dat2$Maple_SurvivalY2<-c()
dat2$Maple_SurvivalY2[is.na(dat2$MapleFinalMass)]<-0 #Converting all those without a final measurement to dead.
dat2$Maple_SurvivalY2[!is.na(dat2$MapleFinalMass)]<-1 #Anything that is not NA (i.e. has a final measurment, is alive)
dat2$Maple_SurvivalY2[dat2$Maple_TotalLeafArea_End==0]<-NA #anything that died in the first year is overwritten as NA 
dat2$Maple_SurvivalY2[!dat2$treatment %in% c("mcnt","m")]<-NA


#Creating a column to indicate whether maples survived in year 1 or not.
dat2$Maple_SurvivalY1<-c()
dat2$Maple_SurvivalY1[dat2$Maple_TotalLeafArea_End==0]<-0 #anything with a value of 0 is dead
dat2$Maple_SurvivalY1[is.na(dat2$Maple_TotalLeafArea_End)]<-NA #anything with NA is unknown
dat2$Maple_SurvivalY1[dat2$Maple_SurvivalY2==1]<-1 #Those with an NA will be overwritten if i have a record of their size in year two. 
dat2$Maple_SurvivalY1[dat2$Maple_TotalLeafArea_End>0]<-1 #anything with a value greater than zero is alive

#This Genotype was NA for maple total leaf area, but we know that it is dead. 
dat2$Maple_SurvivalY1[dat2$Tag=="e|CBMCK1-1-0|N|49"]<-0

#Creating a new fecundity collumn that has zeros for dead individuals 
dat2$GM_Fecundity2<-dat2$GM_Fecundity+0.05

#assigning those that didnt survive to zero.
dat2$GM_Fecundity2[dat2$Bolt_Survival==0]<-0

```


#Removing dead individuals and dead competitors from the analysis. 
```{r}

#Removing those with dead competitors from the garlic mustard treatment. ("e|JBCHY1-1-50|Q|240") did not die, we are simply missing the final measurement for it.
dead_competitors<-dead %>% filter(treatment=="gm",Tag!="e|JBCHY1-1-50|Q|240") %>% select(comp_number)

#Removing those with dead competitors from the analysis. 
dat2<-dat2 %>% filter(!comp_number %in% dead_competitors$comp_number)
dat<-dat %>% filter(!comp_number %in% dead_competitors$comp_number)

#Removing dead individuals from the analysis. 
dat2<-dat2[dat2$GreenhouseSurvival==1,]

#Removing those with dead maples from the analysis
dat2<-dat2[dat2$Maple_SurvivalY1==1 | is.na(dat2$Maple_SurvivalY1),]

```


#Generating PCA for Glucosinolate and Chlorophyll
```{r}

pcaGlucCor<-prcomp(~Standardize(ChlorA)+Standardize(gluc_Conc),data=dat2,na.action=na.omit)
biplot(pcaGlucCor)
pcaGlucCor
summary(pcaGlucCor)

#Loading to data frame.
prediction<-as.data.frame(predict(pcaGlucCor))

#addings PCs to the data frame. 
df2<-tibble::rownames_to_column(prediction, "rownumber")
dat2[df2$rownumber,"PCCG_1"]<-df2$PC1
dat2[df2$rownumber,"PCCG_2"]<-df2$PC2

hist(dat2$PCCG_1)
```

#PCA of GM SIZE in the second year. 
```{r}
#Changing dead individuals to zero. 
dat2$GM_StemHeight_Bolt[which(dat2$GM_StemHeight_Bolt=="Dead")]<-NA
dat2$GM_Leaf_Number_Bolt[which(dat2$GM_Leaf_Number_Bolt=="Dead")]<-NA
dat2$Larg_Leaf_Len_Bolt[which(dat2$Larg_Leaf_Len_Bolt=="Dead")]<-NA
dat2$Larg_Leaf_Wid_Bolt[which(dat2$Larg_Leaf_Wid_Bolt=="Dead")]<-NA

#Making data numeric
dat2$GM_StemHeight_Bolt<-as.numeric(dat2$GM_StemHeight_Bolt)
dat2$GM_Leaf_Number_Bolt<-as.numeric(dat2$GM_Leaf_Number_Bolt)
dat2$Larg_Leaf_Len_Bolt<-as.numeric(dat2$Larg_Leaf_Len_Bolt)
dat2$Larg_Leaf_Wid_Bolt<-as.numeric(dat2$Larg_Leaf_Wid_Bolt)

#Performing principal component analysis
pca<-prcomp(~GM_StemHeight_Bolt+GM_Leaf_Number_Bolt+Larg_Leaf_Len_Bolt+Larg_Leaf_Wid_Bolt,data=dat2,scale.=T,na.action=na.omit)
summary(pca)

#Assignign PCA bolt size data to the main data frame from analysis
prediction<-as.data.frame(predict(pca))
df<-tibble::rownames_to_column(prediction, "rownumber")
dat2[df$rownumber,"PC1BoltSize"]<-df$PC1
```


#PCA of Initial maple size
```{r}
#Creating a maple data frame
Maple<-dat2[dat2$treatment=="m"|dat2$treatment=="mcnt",]

#b|EFCC2-4-80|Q|144 and f|JBCHY1-1-50|Q|247,e|CBMCK1-1-0|N|49, e|JWBOY-2-80|Q|264 are simply not in the datafile. Nothing to do there - they will be deleted from the analysis. These genotypes are either dead, or we missed them when conducting the sampling.
Maple<-Maple[!is.na(Maple$Maple_StemHeight_End),]
Maple$treatment<-factor(Maple$treatment,levels = c("m","mcnt"))

#Selecting variables to use in the PCA (All initial and final maple measurements which could indicate performance)
PCAMaple<-Maple %>% select(maple_height_0,maple_leaf_length_0,maple_leaves_0,Maple_StemHeight_End,Maple_LeafNum_End,Maple_TotalLeafArea_End)

#Standardizing all variables.
PCAMaple<-data.frame(apply(PCAMaple,2,Standardize))

#Performing PCA model of initial maple size
pcaModelTotal<-prcomp(PCAMaple)
summary(pcaModelTotal)
pcaModelTotal

#All variables are correlated with the PC1 loading. 
plot(predict(pcaModelTotal)[,1]~PCAMaple$Maple_TotalLeafArea_End)
plot(predict(pcaModelTotal)[,1]~PCAMaple$maple_height_0)
plot(predict(pcaModelTotal)[,1]~PCAMaple$maple_leaf_length_0)
plot(predict(pcaModelTotal)[,1]~PCAMaple$maple_leaves_0)

#Adding in PC1 values of initial maple size to main maple data frame.
Maple$PC1Tot<-predict(pcaModelTotal)[,1]

#Creating a new data frame without maple controls (to be used in models that do not include maple treatment as a variable.) 
MapleModel<-Maple %>% filter(treatment=="m")
```


 
#What influences performance? 
```{r}
#Making fungal damage a factor for analyses
dat2$WhiteFungLogis<-as.factor(dat2$WhiteFungLogis)

#Modelling random effects.
fitfull<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam*WhiteFungLogis*ThripsDam+Standardize(Fern)+RGR1+(1|Family)+(1|gh_bench), data=dat2)

fitfull1<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam*WhiteFungLogis*ThripsDam+Standardize(Fern)+RGR1+(1|gh_bench), data=dat2)

fitfull2<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam*WhiteFungLogis*ThripsDam+Standardize(Fern)+RGR1+(1|Family), data=dat2)

summary(fitfull)
#Is family important? 
anova(fitfull,fitfull1) #No
#Is gh bench important? 
anova(fitfull,fitfull2) #Yes, gh_bench predicts performance. 


#Modelling fixed effects. 

#IS fern important? 
  fitfull1<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam*WhiteFungLogis*ThripsDam+Standardize(Fern)+RGR1+(1|gh_bench), data=dat2)
  fit2<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam*WhiteFungLogis*ThripsDam+RGR1+(1|gh_bench), data=dat2)
  anova(fitfull1,fit2) #yes

fit2<-update(fitfull1,~.-ThripsDam:BlackPathDam:WhiteFungLogis)
anova(fitfull1,fit2) #Not a significant three way interaction.

fit3<-update(fit2,~.-BlackPathDam:WhiteFungLogis)
anova(fit3,fit2) #There is not a significant two way interaction, 

fit4<-update(fit3,~.-BlackPathDam:ThripsDam)
anova(fit4,fit3)
#There is not a significant interaction between black path dam and thrips dam. 

fit5<-update(fit4,~.-WhiteFungLogis:ThripsDam)
anova(fit5,fit4) #There is not a significant whitefung dam and thrips dam interaction. 
summary(fit5)

#IS thrips dam significant?
fit11<-glmmTMB(Standardize(GM_TotalLeaf_Area) ~ treatment*PCCG_1+treatment*PCCG_2 + BlackPathDam +  WhiteFungLogis + ThripsDam  + RGR1 +Fern+(1 | gh_bench),data=dat2[!is.na(dat2$ThripsDam),])
fit12<-glmmTMB(Standardize(GM_TotalLeaf_Area) ~ treatment*PCCG_1+treatment*PCCG_2 + BlackPathDam +  WhiteFungLogis + RGR1+Fern+ (1 | gh_bench) ,data=dat2[!is.na(dat2$ThripsDam),])
anova(fit11,fit12) #No.

#Is  White Path dam significant
fit6<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam+WhiteFungLogis+RGR1+Fern+(1|gh_bench), data=dat2[!is.na(dat2$WhiteFungLogis),])
fit8<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam+RGR1+Fern+(1|gh_bench), data=dat2[!is.na(dat2$WhiteFungLogis),])
anova(fit6,fit8) #No

#Is  Black Path dam significant
fit5<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam+WhiteFungLogis+RGR1+Fern+(1|gh_bench), data=dat2[!is.na(dat2$BlackPathDam),])
fit7<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+WhiteFungLogis+RGR1+Fern+(1|gh_bench), data=dat2[!is.na(dat2$BlackPathDam),])
anova(fit5,fit7) #Yes

#IS RGR1 significant?

fit4<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam+RGR1+Fern+(1|gh_bench), data=dat2[!is.na(dat2$RGR1),])
fit5<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*PCCG_1+treatment*PCCG_2+BlackPathDam+Fern+(1|gh_bench), data=dat2[!is.na(dat2$RGR1),])
anova(fit5,fit6) # No

#IS the interaction between treatment and PCCG_2 significant?
fit6<-update(fit5,~.-treatment:PCCG_2)
anova(fit6,fit5) #No. 


#IS the interaction between treatment and PCCG_1 significant?
fit7<-update(fit6,~.-treatment:PCCG_1)
anova(fit7,fit6) #Yes

#IS PCCG_2 significant? 
fit8<-update(fit7,~.-PCCG_2)
anova(fit8,fit7) #No. 

#Best Model is: 
fit6<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*Standardize(PCCG_1)+Standardize(Fern)+Standardize(BlackPathDam)+(1|gh_bench),  data=dat2)
summary(fit6)

plot(residuals(fit6)~fitted(fit6))
hist(residuals(fit6),breaks=20)

#Perform Permutation test on this to revalidate the p values of the terms in the interaction. 

```


#Testing perfromance on residuals of leaf traits controlling for leaf size 
Reassessing PCCG_1 interaction after controlling for leaf area in PCCG_1. 
```{r}
#Best model
fit6<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*Standardize(PCCG_1)+Standardize(Fern)+Standardize(BlackPathDam)+(1|gh_bench),  data=dat2) 

#Obtaining clean data frame
#Removing Na's and making new dataframe with NAs excluded
datPlot<-dat2[!is.na(dat2$PCCG_1)&!is.na(dat2$BlackPathDam)&!is.na(dat2$gh_bench)&!is.na(dat2$Fern)&!is.na(dat2$GM_Leaf_Area),]



#For PCCG_1, Leaf Quality, obtaining the values of PCCG_1 after controlling for leaf area. 
fit<-glmmTMB(Standardize(PCCG_1)~Standardize(GM_Leaf_Area),data=datPlot)
fitResi<-residuals(fit)
datPlot$CGFResi<-as.single(fitResi)

#Assessing significance of interaction. 
fit6<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment*Standardize(CGFResi)+Standardize(Fern)+Standardize(BlackPathDam)+(1|gh_bench),  data=datPlot)

fit7<-glmmTMB(Standardize(GM_TotalLeaf_Area)~treatment+Standardize(CGFResi)+Standardize(Fern)+Standardize(BlackPathDam)+(1|gh_bench),  data=datPlot)
anova(fit6,fit7) #Interaction is highly significant. p = 0.001

#Therefore, the  analysis without controlling for leaf area is similar to that with it controlled for.
summary(fit6)
```

#Performance visualization with other factors controlled for
```{r}
source("GGPlot_Themes.R")

###
#Fitting a residual model
###

#The mean standardized selection gradient. 
fit6<-glmmTMB(Standardize(GM_TotalLeaf_Area,meanSTD = T)~treatment*Standardize(PCCG_1)+Standardize(BlackPathDam)+Standardize(Fern)+(1|gh_bench),  data=dat2) #Most gluc is correlated with performance, but not causing it through allelopathy? idk. 
summary(fit6)

#Removing Na's and making new dataframe with NAs excluded
datPlot<-dat2[!is.na(dat2$PCCG_1)&!is.na(dat2$BlackPathDam)&!is.na(dat2$gh_bench)&!is.na(dat2$Fern),]


#Obtaining residuals from a model without the treatment*leafquality interaction
fit6<-glmmTMB(Standardize(GM_TotalLeaf_Area,meanSTD = T)~Standardize(BlackPathDam)+Standardize(Fern)+(1|gh_bench), data=datPlot)
summary(fit6)

#adding in residuals to the dataframe. 
fitResi<-residuals(fit6)
datPlot$GMSizeResi<-as.single(fitResi)

#Modelling the residuals against the interaction
fit7<-glmmTMB(GMSizeResi~treatment*Standardize(PCCG_1), data=datPlot)
summary(fit7) #The significance is still there. 


###
#Setting plotting parameters
###

aloneSlope<-function(x){
  #y= 0.07142*x+ 0.34161
    y=( -0.07025)*x+ 0.22261
  return(y)
}
mapleSlope<-function(x){
  y=( --0.07025 +0.17063  )*x+0.22261   -0.15270
  return(y)
}

mustardSlope<-function(x){
  #y=( 0.07142+0.03584)*x+0.34161-0.61888#Non significant slope
    y=(-0.07025+0.09801)*x+0.22261-0.47588 #Non significant slope
  return(y)
}

#Standardizing variables.
datPlot$PCCG_1S<-Standardize(datPlot$PCCG_1)

#Obtaining minimum and maximum values of leaf quality in each treatment.
minM<-min(datPlot$PCCG_1S[datPlot$treatment=="m"],na.rm = T)
maxM<-max(datPlot$PCCG_1S[datPlot$treatment=="m"],na.rm = T)

minA<-min(datPlot$PCCG_1S[datPlot$treatment=="a"],na.rm = T)
maxA<-max(datPlot$PCCG_1S[datPlot$treatment=="a"],na.rm = T)

minG<-min(datPlot$PCCG_1S[datPlot$treatment=="gm"],na.rm = T)
maxG<-max(datPlot$PCCG_1S[datPlot$treatment=="gm"],na.rm = T)

#Removing maple control
datPlot<-datPlot[datPlot$treatment!="mcnt",]


###
#Plotting
###

TLATiff<-ggplot(datPlot)+
  geom_point(aes(y=GMSizeResi,x=PCCG_1S,colour=treatment),size=1)+
  geom_segment(x=minA,xend=maxA,y=aloneSlope(minA),yend=aloneSlope(maxA),colour="#009E73",size=1.5)+
    geom_segment(x=minM,xend=maxM,y=mapleSlope(minM),yend=mapleSlope(maxM),colour="#E69F00",size=1.5)+
  geom_segment(x=minG,xend=maxG,y=mustardSlope(minG),yend=mustardSlope(maxG),colour="#56B4E9",size=1.5)+theme_simple_multiCol_First()+
  ylab(bquote(bold("Rosette Size Residuals")))+xlab("General Glucosinolate and Chlorophyll investment (σ)")+
  scale_y_continuous(breaks=seq(-2,3,by=0.5))+
  scale_x_continuous(breaks=seq(-5,5,by=1))+

  scale_colour_manual(values=c("#009E73","#56B4E9","#E69F00"),labels=c("Alone","Intraspecific","Interspecific"))

tiff("Selection_Figures/GCInvestement_VS_RosetteSizeResiduals.tiff", units="in", width=8, height=6, res=300)
TLATiff
dev.off()

```



#Testing performance on residuals of leaf traits controlling for leaf size 
Reassessing PCCG_1 interaction after controlling for leaf area in PCCG_1. 
```{r}
#Removing Na's and making new dataframe with NAs excluded
datPlot<-dat2[!is.na(dat2$GM_Leaf_Area)&!is.na(dat2$PCCG_1)&!is.na(dat2$Fern)&!is.na(dat2$Row_Field)&!is.na(dat2$Bolt_Survival),]

#For PCCG_1, Leaf Quality, obtaining the values of PCCG_1 after controlling for leaf area. 
fit<-glmmTMB(Standardize(PCCG_1)~Standardize(GM_Leaf_Area),data=datPlot)
fitResi<-residuals(fit)
datPlot$CGResi<-as.single(fitResi)

#Assessing significance of interaction. 

fit1<- glmmTMB(Bolt_Survival ~ treatment*Standardize(CGResi) + Standardize(Fern) +  
    (1 | Family) + (1 | Row_Field) ,data=datPlot, family="binomial")
fit2<- glmmTMB(Bolt_Survival ~ treatment+Standardize(CGResi) + Standardize(Fern) +  
    (1 | Family) + (1 | Row_Field) ,data=datPlot, family="binomial")

anova(fit1,fit2) #Interaction is close to significance after controlling for leaf area of sampled leaf. ... but not significant. Therefore, i should neglect it? 

summary(fit1)
```


#Modelling total relative fitness.
--did this wrong. the log doesnt work on 0 must be plus 1. 
```{r}
####
#Testing model fit
####

datPlot<-dat2[!is.na(dat2$GM_Fecundity2)&!is.na(dat2$PCCG_1)&!is.na(dat2$Fern)&!is.na(dat2$BlackPathDam)&!is.na(dat2$RGR1)&!is.na(dat2$PC1BoltSize),]

fit<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2)
hist(residuals(fit),breaks=20)
plot(residuals(fit)~fitted(fit))
plot(fitted(fit),log(datPlot$GM_Fecundity2+1))+abline(a=0,b=1) #This is actually a pretty good model. 
shapiro.test(residuals(fit)) #The fit is not that bad. 


####
#Modelling
####

#Maximum model ... 
fit<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family)+(1|Col_Field),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit2<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit3<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family)+(1|gh_bench),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit4<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit5<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Row_Field),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit6<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

#IS column in field significant?
anova(fit,fit4) # No

#IS row in field significant?
anova(fit2,fit4) #No

#IS gh_bench  significant?
anova(fit3,fit4) #No.

#IS family  significant?
anova(fit5,fit2) #No... but close - 0.07

###Modelling fixed effects 

#IS Black Path  dam significant?
fit1<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$BlackPathDam),])
fit2<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$BlackPathDam),])
anova(fit1,fit2) #No


#IS Fern significant?
fit2<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$Fern),])
fit3<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$Fern),])
anova(fit2,fit3) #No


###
# Testing life history data now
###

#Is RGR significant?
fit3<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$RGR1),])
fit4<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$RGR1),])
anova(fit3,fit4) # yes


#Is Total leaf area (year 1) significant?
fit3<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(PC1BoltSize)+Standardize(RGR1),data=dat2[!is.na(dat2$GM_TotalLeaf_Area),])
fit4<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(PC1BoltSize)+Standardize(RGR1),data=dat2[!is.na(dat2$GM_TotalLeaf_Area),])
anova(fit3,fit4) #No

#Is bolt size?
fit4<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$PC1BoltSize),])
fit5<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1),data=dat2[!is.na(dat2$PC1BoltSize),])
anova(fit4,fit5)# Yes it is.... very but perhaps a dumb variable to include beacuse all dead individuals also have 0 bolt size. 


###
# Testing leaf treats now
###
fit5<-glmmTMB(log(GM_Fecundity2+1)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2)


#IS the interaction between treatment and PCCG_2 significant?
fit6<-update(fit5,~.-treatment:PCCG_2)
anova(fit6,fit5) #No. 

#IS PCCG_2 significant? 
fit7<-update(fit6,~.-PCCG_2)
anova(fit7,fit6) #No 

#IS the interaction between treatment and PCCG_1 significant?
fit8<-update(fit7,~.-treatment:PCCG_1)
anova(fit8,fit7) #No, but close

#Is pccg_1 significant?
fit12<-glmmTMB(log(GM_Fecundity2+1)~treatment+PCCG_1+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$PCCG_1),])
fit13<-glmmTMB(log(GM_Fecundity2+1)~treatment +Standardize(PC1BoltSize),data=dat2[!is.na(dat2$PCCG_1),])
anova(fit12,fit13)# No.

#Assessing PCCG_1 interaction without boltsize.
 fit10<-glmmTMB(log(GM_Fecundity2+1) ~ treatment * PCCG_1  ,data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(log(GM_Fecundity2+1) ~ treatment + PCCG_1 ,data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 0.15

#Assessing PCCG_2 interaction without boltsize.
 fit10<-glmmTMB(log(GM_Fecundity2+1) ~ treatment * PCCG_2  ,data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(log(GM_Fecundity2+1) ~ treatment + PCCG_2 ,data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 0.15


#Best Model
fit13<-glmmTMB(log(GM_Fecundity2+1)~treatment +Standardize(PC1BoltSize),data=dat2)
summary(fit13)


```


#What affects maple performance year 1? 
Need to know this to determine what goes into the permutation test in path analysis. 
```{r}
#Is bench important? 
fit<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2+(1|gh_bench), data=MapleModel)
fit2<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2, data=MapleModel)
anova(fit,fit2) #No it is not.

#Modelling fixed effects. 
fit<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2+MapleDamage+Family+GM_TotalLeaf_Area+Fern, data=MapleModel)
summary(fit) 

fit2<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2+MapleDamage+GM_TotalLeaf_Area+Fern, data=MapleModel)
anova(fit,fit2) #Family not significant. 
summary(fit2)

fit3<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2+MapleDamage+Fern, data=MapleModel)
anova(fit2,fit3) #Total leaf area not significant. 

#IS PCCG_2 significant?
fit5<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+MapleDamage+Fern+PCCG_1, data=MapleModel)
anova(fit3,fit5) #Yes it is.... Very interesting. This is the glucosinolate ratio!!


#IS PCCG_1 significant?
fit5<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+MapleDamage+Fern+PCCG_1+PCCG_2, data=MapleModel)

fit6<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+MapleDamage+Fern+PCCG_2, data=MapleModel)
anova(fit6,fit5) #Yes, this is also significant, which was the variable with a treatment interaction in the first place. 

#IS damage significant?
fit7<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2+Fern, data=MapleModel)
anova(fit7,fit5) #Yes it is. 

#IS Fern significant?
fit8<-glmmTMB(Maple_TotalLeafArea_End~PC1Tot+PCCG_1+PCCG_2+MapleDamage, data=MapleModel)
anova(fit5,fit8) #No it is not. 

#IS initial size significant?
fit9<-glmmTMB(Maple_TotalLeafArea_End~PCCG_1+PCCG_2+MapleDamage+Fern, data=MapleModel)
anova(fit9,fit8) #Yes it is. Very much so. 


#The best model is 
fit3<-glmmTMB(Standardize(Maple_TotalLeafArea_End)~Standardize(PC1Tot)+Standardize(PCCG_1)+Standardize(PCCG_2)+Standardize(MapleDamage), data=MapleModel)
summary(fit3)


plot(residuals(fit3,type="pearson"),fitted(fit3))

plot(residuals(fit3,type="pearson"))
qqnorm(residuals(fit3,type="pearson"))
```



#What affects maple performance year 2? 
```{r}
MapleModel$Bolt_Survival<-as.factor(MapleModel$Bolt_Survival)

#Is bench important? 
fit<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2+(1|gh_bench), data=MapleModel)
fit2<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2, data=MapleModel)
anova(fit,fit2) #No it is not.

#Is col field important? 
fit<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2+(1|Col_Field), data=MapleModel[!is.na(MapleModel$Col_Field),])
fit2<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2, data=MapleModel[!is.na(MapleModel$Col_Field),])
anova(fit,fit2) #No it is not.

#Is row field important? 
fit<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2+(1|Row_Field), data=MapleModel[!is.na(MapleModel$Row_Field),])
fit2<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2, data=MapleModel[!is.na(MapleModel$Row_Field),])
anova(fit,fit2) #Yes it is, p=0.019


#Modelling fixed effects. 
fit<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2+MapleDamage+Family+GM_TotalLeaf_Area+Fern+Bolt_Survival+(1|Row_Field), data=MapleModel)

fit2<-glmmTMB(log(MapleFinalMass)~PC1Tot+PCCG_1+PCCG_2+MapleDamage+GM_TotalLeaf_Area+Fern+Bolt_Survival+(1|Row_Field), data=MapleModel)
anova(fit,fit2) #Family not significant. 
summary(fit2)

fit3<-update(fit2,~.-GM_TotalLeaf_Area)
anova(fit2,fit3) #Total leaf area is  significant. 

#Is PCCG_2 significant?
fit4<-update(fit2,~.- PCCG_2)
anova(fit2,fit4) #No


#Is Bolt_Survival significant?
fit5<-glmmTMB(log(MapleFinalMass) ~ PC1Tot + PCCG_1 + MapleDamage +  
    GM_TotalLeaf_Area + Fern + Bolt_Survival+(1|Row_Field),data=MapleModel[!is.na(MapleModel$Bolt_Survival),])
fit6<-update(fit5,~.- Bolt_Survival)
anova(fit5,fit6) #No

#IS maple damage significant? 
fit6<-glmmTMB(log(MapleFinalMass) ~ PC1Tot + PCCG_1 + MapleDamage +  
    GM_TotalLeaf_Area + Fern+(1|Row_Field) ,data=MapleModel)
fit7<-glmmTMB(log(MapleFinalMass) ~ PC1Tot + PCCG_1  +  
    GM_TotalLeaf_Area + Fern+(1|Row_Field) ,data=MapleModel)
anova(fit6,fit7)#No.

#IS PCCG_1?
fit7<-glmmTMB(log(MapleFinalMass) ~ PC1Tot + PCCG_1  +  
    GM_TotalLeaf_Area + Fern+(1|Row_Field) ,data=MapleModel[!is.na(MapleModel$PCCG_1),])
fit8<-update(fit7,~.-PCCG_1)
anova(fit7,fit8) #no

#Is Fern
fit9<-glmmTMB(log(MapleFinalMass) ~ PC1Tot   +  
    GM_TotalLeaf_Area + Fern+(1|Row_Field) ,data=MapleModel[!is.na(MapleModel$Fern),])
fit10<-update(fit9,~.-Fern)
anova(fit9,fit10) #no Fern did not have effects on maple at all. 


#Is GM size in second year important? 
fit9<-glmmTMB(log(MapleFinalMass) ~ PC1Tot   +  
    GM_TotalLeaf_Area +PC1BoltSize+(1|Row_Field) ,data=MapleModel[!is.na(MapleModel$PC1BoltSize),])
fit10<-update(fit9,~.-PC1BoltSize)
anova(fit9,fit10) #GM Size in second year is very close to significant at p=0.054, but not significant.. 


#Is maple initial size significant?
fit9<-glmmTMB(log(MapleFinalMass) ~ Standardize(PC1Tot)  +
   Standardize( GM_TotalLeaf_Area )+(1|Row_Field) ,data=MapleModel[!is.na(MapleModel$PC1Tot),])
fit10<-update(fit9, ~.-Standardize( PC1Tot ))
anova(fit9,fit10) #Yes.

#Best model is
fit9<-glmmTMB(log(MapleFinalMass) ~ Standardize(PC1Tot)  +
   Standardize( GM_TotalLeaf_Area ) +(1|Row_Field),data=MapleModel)
summary(fit9)

plot(residuals(fit9,type="pearson"),fitted(fit9))

plot(residuals(fit9,type="pearson"))
qqnorm(residuals(fit9,type="pearson"))


```




#Reassignigng greenhouse bench for use in the lavaan model
Nominal variables not accepted. Determining where the real differences lie with metho of crawley from the R book. 
```{r}
#Indirect effect of leaf traits on performance
fitBench1<-lm(GM_TotalLeaf_Area~as.factor(gh_bench),data=dat2)
summary(fitBench)
f<-aov(fitBench)
TukeyHSD(f)
#With maple model, they were all different than 1. 

#lets try with merging groups 2-5 and seeing if this changes anything
dat2$gh_bench2<-dat2$gh_bench

dat2$gh_bench2[dat2$gh_bench2 %in% c("2","3","4","5")]<-"0"


#with only two levels
fitBench2<-lm(GM_TotalLeaf_Area~as.factor(gh_bench2),data=dat2)

#with 5 levels 
fitBench1<-lm(GM_TotalLeaf_Area~as.factor(gh_bench),data=dat2)

anova(fitBench2,fitBench1) #There is information lost, but the following is performed only on
#individuals in the maple model, therefore i will test this. 

MapleModel2<-dat2[dat2$treatment=="m",]
#with only two levels
fitBench2<-lm(GM_TotalLeaf_Area~as.factor(gh_bench2),data=MapleModel2)
summary(fitBench2)
#with 5 levels 
fitBench1<-lm(GM_TotalLeaf_Area~as.factor(gh_bench),data=MapleModel2)

anova(fitBench2,fitBench1) #This difference is not significant, therefore i can just include
#one variable for greenhouse bench classifying as either bench 1 or bench 2. 

```

#Functions for easy permutation test with parallelization
```{r}
library(parallel)

#Function to provide a new data set filled with columns of permutations of a given vector.  
NewData<-function(data,Column_Name=NA){ #Function to build a data frame with collumns representing permutations of the given vector.
  
  #Making cloumn name a string
#Column_Name<-deparse(substitute(Column_Name))

# stopping if column name not entered
      if(is.na(Column_Name)){
     stop("No column name provided, must be a character string")
    }

#   #Removing Rows with NA's for the focal column. 
   data2<- data[!is.na(data[[Column_Name]]),]

   #Sample column
       Random<-sample(data2[[Column_Name]],replace=F)
# 
    #
   data2[,Column_Name]<-Random
  return(data2)
 }



#Function to run the SEM model and obtain the output of interest from a data frame in a list 
Model_Over_List<-function(Formula, data_frame_as_list,L_or_A_pply="lapply", ...){
  
  if(L_or_A_pply=="apply"){
      Data<-as.data.frame(data_frame_as_list) #Modify list data to be in a data frame format
  }
  
  else
  Data=data_frame_as_list
  
 fit<-sem(Formula,data=Data, ...) #Model with the data

 invisible(capture.output(b<-summary(fit,standardize=T)[[1]])) #Summarize model 

Z<-b[b$lhs=="indirect","z"]#Extract coefficient of interest (z value)
 
  return(Z)
}


#This function is a wrapper of the previous two and performs a permutation test with the supplied parameters 
Permulation_Test<-function(Model_Formula,Data,Variable,Replication){
  
  #Obtaining name of Variable from environment
    Variable<-substitute(Variable)
  
   #Determining the real z value
   Real_Z<-Model_Over_List(Model_Formula,data_frame_as_list=Data)

#Obtaining data frames with desired replication
 Data_Frames<-replicate(Replication,NewData(Data,Variable),simplify=F)
# 
# Modeling desired formula over each data frame with a random permutation
 random_Z<-unlist(mclapply(Data_Frames,Model_Over_List,Formula = Model_Formula))
 
# #Obtaining p value
 p_Val<-length(random_Z[abs(random_Z)>abs(Real_Z)])/length(random_Z) #The indirect p value is 0.0085 which is a indirect effect of PPCG_2 on performance. 
 
 #Returing a histogram of z values
 p<-ggplot()+
   geom_histogram(aes(x=random_Z),bins = 50) +
   geom_vline(aes(xintercept=Real_Z),colour="red")
 
 return(list(Real_Z,p_Val,random_Z,p))

}


```


#Performing permutation tests for the indirect effect of PCCG_1 on performance
I am only doing the permutation tests including maple performance in year 1 because this is where both 

#Inkscape.
inkscape.org
save as svg. -- keep Add in fitness to this model? to "flush it out"


PCCG_1 and PCCG_2 were shown to impact maple fitness. 
Model Formula
```{r}
library(lavaan)
library(semPlot)


#Standardizing variables
MapleModel$GM_TotalLeaf_AreaS<-Standardize(MapleModel$GM_TotalLeaf_Area)
MapleModel$Maple_TotalLeafArea_EndS<-Standardize(MapleModel$Maple_TotalLeafArea_End)
MapleModel$BlackPathDamS<-Standardize(MapleModel$BlackPathDam)

#Modifying the gh_bench variable
MapleModel$gh_bench<-as.numeric(MapleModel$gh_bench)

MapleModel$gh_bench2<-MapleModel$gh_bench

MapleModel$gh_bench2[MapleModel$gh_bench2 %in% c(2,3,4,5)]<-0

MapleModel$gh_bench2



#Indirect effect of leaf traits on performance

MapleFormula_1_1 <- '
Maple_TotalLeafArea_EndS ~ PC1Tot+B1*PCCG_1 + MapleDamage + PCCG_2

GM_TotalLeaf_AreaS ~ B3*Maple_TotalLeafArea_EndS + BlackPathDamS +Fern +PCCG_2+ PCCG_1+ gh_bench2

indirect := B1 * B3

'
fit<-sem(MapleFormula_1_1,data=MapleModel)

summary(fit,standardize=T)
# Indirect effect including the direct influence 0.041    0.018    2.303    0.021
#Indirect effect without including the direct influence  0.046    0.018    2.524    0.012

semPaths(fit,"path",layout = "circle",edge.label.cex=.9, curvePivot = TRUE)
semPaths(fit,title=FALSE, exoVar = FALSE, exoCov = FALSE)
semPaths(fit,"std", edge.label.cex = 0.5, exoVar = FALSE, exoCov = FALSE)

Permulation_Test(MapleFormula_1_1,MapleModel,"PCCG_1",2000)
#Pvalue is 0.009 for the indirect effect of PCCG_1 on gm performance through maple. 



#If Indirect effect of leaf traits on fitness. 
MapleFormula_1_3 <- '
Maple_TotalLeafArea_EndS ~ PC1Tot+B1*PCCG_1 + MapleDamage + B2*PCCG_2 

GM_Fecundity2L ~ B3*Maple_TotalLeafArea_EndS +PCCG_2 +PCCG_1

indirect := B1 * B3 
'

out<-Permulation_Test(MapleFormula_1_3,MapleModel,"PCCG_1",2000)
#Pvalue is 0.0455 for the indirect effect of PCCG_1 on gm fitness through maple. 


#If Indirect effect of leaf traits on all relative fitness 
MapleModel$GM_Fecundity3<-MapleModel$GM_Fecundity2/mean(MapleModel$GM_Fecundity2,na.rm=T)

MapleFormula_1_4 <- '
Maple_TotalLeafArea_EndS ~ PC1Tot+B1*PCCG_1 + MapleDamage + B2*PCCG_2 

GM_Fecundity3 ~ B3*Maple_TotalLeafArea_EndS +PCCG_2 +PCCG_1

indirect := B1 * B3 
'

out<-Permulation_Test(MapleFormula_1_4,MapleModel,"PCCG_1",2000)
#Pvalue is 0.2265 for the indirect effect of PCCG_1 on total gm relative fitness through maple. 


semPaths(fit,"path",layout = "circle",edge.label.cex=.9, curvePivot = TRUE)
semPaths(fit,title=FALSE, exoVar = FALSE, exoCov = FALSE)
semPaths(fit,"std", edge.label.cex = 0.5, exoVar = FALSE, exoCov = FALSE)


```

#Visualizing path analysis
```{r}
semPaths(fit,"path",layout = "circle",edge.label.cex=.9, curvePivot = TRUE)
semPaths(fit,title=FALSE, exoVar = FALSE, exoCov = FALSE)


semPaths(fit,"std", layout = "tree", exoVar = F, exoCov = FALSE,nCharNodes=0,sizeMan = 10,sizeInt2=20,style="lisrel",label.prop=0.9,esize=10)


semPaths(fit,"std", layout = "tree", exoVar = F, exoCov = FALSE,nCharNodes=0,sizeMan = 10,style="lisrel")

```


#Using a manual ggraph
```{r}
library(ggraph)
library(igraph)


#Constructing data frame of paths
b<-summary(fit,standardize=T)[[1]]
b<-b %>% filter(exo==0) %>% select(from=rhs,to=lhs,est,pvalue)
b<-b %>% filter(to!="indirect")

#Defining the whether the relationship is positive or negative.
defineColour<-function(x){
x[x<0]<-"Negative"
x[!grepl("Negative",x)]<-"Positive"
  return(x)
}
b$PosNeg<-defineColour(b$est)


#Creating names for the path diagram
Vert<-data.frame(name=append(unique(b$to),unique(b$from)))
Vert<-Vert[!duplicated(Vert$name),]


#Converting to a graph-able object
SGg<-graph_from_data_frame(b,directed=T)
# SGg
# 

#Custom layout 

#Creating a dummy layout list to work with 
lay = create_layout(SGg, layout ="fr" )

#Importing the x and y data point i want
Lay<-read.csv("CustomLayout.csv")

#Replacing the data point in lay with the ones i want in Lay
lay$x<-Lay$x
lay$y<-Lay$y

#Graphing
set_graph_style(plot_margin = margin(1,1,1,1))

ggraph(lay)  +

 geom_edge_link(
   aes(start_cap = label_rect(node1.name), end_cap = label_rect(node2.name), width=abs(est),color=PosNeg,alpha=-pvalue),
   
    arrow = arrow(type = "closed", length = unit(3, 'mm'))) + 
  
  
    geom_node_text(aes(label = name)) 
 # theme_graph()

summary(fit)

```




```{r}
#### an example

# read edges and nodes
nodes = read.csv("dolphin_nodes.csv")
edges = read.csv("dolphin_edges.csv")
n = nrow(nodes)
m = nrow(edges)

# mutate edges and nodes
edge_type = sample(c("love", "friendship"), m, replace = TRUE)
edge_type
edge_weight = runif(m, 1, 10)
edges
edges = mutate(edges, type = edge_type, weight = edge_weight)
edges

nodes
nodes = mutate(nodes, id = 1:n) %>% select(id, everything())
nodes

# degree of nodes (number of ties for each dolphin)
tb = tibble(v = c(1:n, edges$x, edges$y))
tb
d = count(tb, v)$n - 1
d
count(tb, v)

nodes = mutate(nodes, degree = d)
nodes
edges
# create graph from data frames
g = graph_from_data_frame(edges, directed = FALSE, nodes)

lay = create_layout(g, layout = "kk")

ggraph(lay) + 
  geom_edge_link() + 
  geom_node_point() +
  theme_graph()
```


#Performing permutation tests for the indirect effect of PCCG_2 
Model Formula
```{r}

MapleFormula.1 <- '
Maple_TotalLeafArea_EndS ~ PC1Tot+PCCG_1 + MapleDamage + B2*PCCG_2

GM_TotalLeaf_AreaS ~ B3*Maple_TotalLeafArea_EndS + BlackPathDamS + PCCG_2 +PCCG_1  +Fern+gh_bench2

indirect := B2 * B3

'

summary(sem(MapleFormula.1,data=MapleModel)) #The chi square test determined that is is an adequate fit for the data. 
out<-Permulation_Test(MapleFormula.1,MapleModel,"PCCG_2",2000)
#P value is 0.0095 for the indirect effect of PCCG_2 on total gm performance through maple. Need to increase replication for the paper. ... but looks good! 
out[4]

#If Indirect effect of leaf traits on all relative fitness Statistics performed in permutation test below, not logged data. 
MapleModel$GM_Fecundity3<-MapleModel$GM_Fecundity2/mean(MapleModel$GM_Fecundity2,na.rm=T)

MapleFormula.4 <- '
Maple_TotalLeafArea_EndS ~ PC1Tot+B1*PCCG_1 + MapleDamage + B2*PCCG_2 

GM_Fecundity3 ~ B3*Maple_TotalLeafArea_EndS +PCCG_2 +PCCG_1

indirect := B2 * B3 
'

out<-Permulation_Test(MapleFormula.4,MapleModel,"PCCG_2",2000)
#Pvalue is 0.19 for the indirect effect of PCCG_2 on total gm fitness (i.e. relative fitness with survival included) through maple. 
out[[2]]

2.436*-2.667

-1.799

MapleModel$PC1BoltSize



```










#Variance partition analysis

#Fitness and bolt size variance partition analysis 
```{r}

#Function to extract random effect heritabilities from a glmmTMB model. 
Xtract<-function(x,Resi){
  temp<-VarCorr(x)
GXE=temp$cond$`Family:treatment`[[1]]
E=temp$cond$treatment[[1]]
G=temp$cond$Family[[1]]

G_by_E<-GXE/(GXE+E+G+Resi)
Envir<-E/(GXE+E+G+Resi)
Genet<-G/(GXE+E+G+Resi)
data.frame(Type=c("GXE","E","G"),Value=c(G_by_E,Envir,Genet)*100)
}



#Fecundity
fit<-glmmTMB(GM_Fecundity~1+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(GM_Fecundity~1+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(GM_Fecundity~1+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(GM_Fecundity~1+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,5.611e+00) #Large effect of treatment on the values fecundity. 


#Survival 
#some genotypes that were recorded as dead actually grew again from the root to produce a bolt and seeds. I am replacing these with a 1 to designate that they are alive. 


#Conducting analysis on Survival
fit<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|treatment/Family)+(1|Family),data=dat2,family="binomial")
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|treatment)+(1|Family),data=dat2,family="binomial")
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|treatment),data=dat2,family="binomial")
anova(fit2,fit3)#Yes, very strong effect. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Bolt_Survival~as.factor(Row_Field)+(1|Family),data=dat2,family="binomial")
anova(fit2,fit4)#No, Not at all. 

summary(fit)
Xtract(fit,pi^2/3) #Large effect of treatment on the values fecundity. 
df.residual(fit)
pi^2/3


#Bolt Size

#Is there an effect of row? 
fit0.1<-glmmTMB(PC1BoltSize~1+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
fit<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|treatment/Family)+(1|Family),data=dat2)
anova(fit,fit0.1) #Yes there is

#Is there an effect of GXE? 
fit2<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes 

#Is there an effect of treatment? 
fit4<-glmmTMB(PC1BoltSize~as.factor(Row_Field)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,3.163e+00 ) 


```


####Total leaf area RGR, Chlorophyll A and Glucosinoalte
```{r}
#looking at effect with and without black path dam
#Total leaf area. 
fit<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)

#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(GM_TotalLeaf_Area)~as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,0.5898)


#Looking at effect with black path dam.


##Relative growth rate. 
fit<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(RGR1)~as.factor(gh_bench)+GM_Leaf_Len_Initial+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,5.626e-01)

##Chlor A
fit<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#No. 

#Is there an effect of treatment? 
fit4<-glmmTMB(Standardize(ChlorA)~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,8.592e-01)

#Glucosinolate
fit<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. 

#Is there an effect of treatment? 
fit4<-glmmTMB(gluc_Conc~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes. 

summary(fit)
Xtract(fit,0.067131)


```

####Principle component PCCG_1, PCCG_2
```{r}
#########
#PC1
#########
fit<-glmmTMB(PCCG_1~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(PCCG_1~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2) #No.

#Is there an effect of family? 
fit3<-glmmTMB(PCCG_1~GM_Leaf_Area+as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#No... not when assessing in this model. 

#Is there an effect of treatment? 
fit4<-glmmTMB(PCCG_1~GM_Leaf_Area+as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)#Yes, very strong. 

summary(fit)
Xtract(fit,1.37268) #Extremely high environmental effect fot PC1


#########
#PC2 glucosinolate off diagonal. 
#########
fit<-glmmTMB(PCCG_2~as.factor(gh_bench)+(1|treatment/Family)+(1|Family),data=dat2)
summary(fit)
#Is there an effect of GXE? 
fit2<-glmmTMB(PCCG_2~as.factor(gh_bench)+(1|treatment)+(1|Family),data=dat2)
anova(fit,fit2)#No.

#Is there an effect of family? 
fit3<-glmmTMB(PCCG_2~as.factor(gh_bench)+(1|treatment),data=dat2)
anova(fit2,fit3)#Yes. Still highly significant effect of family. 

#Is there an effect of treatment? 
fit4<-glmmTMB(PCCG_2~as.factor(gh_bench)+(1|Family),data=dat2)
anova(fit2,fit4)# No, no effect of treatment at all. 

summary(fit)
Xtract(fit,2.681e-01) #Extremely high Genetic effect for PC2
#Very interesting. 

```


#Fecundity analysis redone with log data (Supplementary)
I have not included flavonoids, nor white path or thrips dam, as these did not effect performance in year 1, therefore, i do not have reason to believe why they would affect fitness in year 2. 
```{r}
#Maximum model ... 
fit<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family)+(1|Col_Field),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit2<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit3<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family)+(1|gh_bench),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit4<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Family),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit5<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize)+(1|Row_Field),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

fit6<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$Col_Field|dat2$Row_Field),])

#IS column in field significant?
anova(fit,fit4) # No

#IS row in field significant?
anova(fit2,fit4) #No

#IS gh_bench  significant?
anova(fit3,fit4) #No.

#IS family  significant?
anova(fit5,fit2) #No, 0.06

###Modelling fixed effects 

#IS Black Path  dam significant?
fit1<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$BlackPathDam),])
fit2<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$BlackPathDam),])
anova(fit1,fit2) #No


#IS Fern significant?
fit2<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$Fern),])
fit3<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$Fern),])
anova(fit2,fit3) #No


###
# Testing life history data now
###

#Is RGR significant?
fit3<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$RGR1),])
fit4<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$RGR1),])
anova(fit3,fit4) # Yes.......


#Is Total leaf area (year 1) significant?
fit3<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$GM_TotalLeaf_Area),])
fit4<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$GM_TotalLeaf_Area),])
anova(fit3,fit4) #No

#Is bolt size?
fit4<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$PC1BoltSize),])
fit5<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1),data=dat2[!is.na(dat2$PC1BoltSize),])
anova(fit4,fit5)# Yes it is.


###
# Testing leaf treats now
###
fit5<-glmmTMB(log(GM_Fecundity)~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2)


#IS the interaction between treatment and PCCG_2 significant?
fit6<-update(fit5,~.-treatment:PCCG_2)
anova(fit6,fit5) #No. 

#IS PCCG_2 significant? 
fit7<-update(fit6,~.-PCCG_2)
anova(fit7,fit6) #No 

#IS the interaction between treatment and PCCG_1 significant?
fit8<-update(fit7,~.-treatment:PCCG_1)
anova(fit8,fit7) #No. 

#IS PCCG_1 significant at all?
 fit10<-glmmTMB(log(GM_Fecundity) ~ treatment + PCCG_1 + Standardize(RGR1) +  
    Standardize(PC1BoltSize),data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(log(GM_Fecundity) ~ treatment  + Standardize(RGR1) +  
    Standardize(PC1BoltSize),data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 

#IS treatment significant at all?
 fit10<-glmmTMB(log(GM_Fecundity) ~ treatment +  Standardize(RGR1) +  
    Standardize(PC1BoltSize),data=dat2)
  fit11<-glmmTMB(log(GM_Fecundity) ~   + Standardize(RGR1) +  
    Standardize(PC1BoltSize),data=dat2)
anova(fit11,fit10) #Yes. treatment is significant 


#IS RGR1 still significant? 
fit11<-glmmTMB(log(GM_Fecundity)~treatment+Standardize(RGR1)+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$RGR1),])
fit12<-glmmTMB(log(GM_Fecundity)~treatment+Standardize(PC1BoltSize),data=dat2[!is.na(dat2$RGR1),])
anova(fit11, fit12) # No



#Best model is: 
fit12<-glmmTMB(log(GM_Fecundity)~treatment+Standardize(PC1BoltSize),data=dat2)
summary(fit12)

#Assessing interaction without boltsize.
 fit10<-glmmTMB(log(GM_Fecundity) ~ treatment * PCCG_1  ,data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(log(GM_Fecundity) ~ treatment + PCCG_1 ,data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 



#Assessing interaction without boltsize.
 fit10<-glmmTMB(log(GM_Fecundity) ~ treatment * PCCG_2  ,data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(log(GM_Fecundity) ~ treatment + PCCG_2 ,data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 



library("PermutateR") #Should add some functionality to obtain many test statistics from the permTest_Custom. #The 

#Should also integrate the two LR functions.

#Assessing interaction without boltsize in permutation test of fitness alone.(PCCG_1)
 fit10<-glmmTMB(GM_Fecundity ~ treatment * PCCG_1  ,data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(GM_Fecundity ~ treatment + PCCG_1 ,data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 

permTest_LR_int(fit10,"treatment:PCCG_1","PCCG_1","Chisq",20)
#Simulated p value is 0.1275 with the LR method. Therefore, not significant. no need to test PCCG_2 as that one had an even higher p value. 


#Assessing interaction without boltsize in permutation test of fitness alone (PCCG_2)
 fit10<-glmmTMB(GM_Fecundity ~ treatment * PCCG_2  ,data=dat2[!is.na(dat2$PCCG_1),])
  fit11<-glmmTMB(GM_Fecundity ~ treatment + PCCG_2 ,data=dat2[!is.na(dat2$PCCG_1),])
anova(fit11,fit10) #No. 

```



#Survival analysis (Supplementary)
```{r}
#Maximum model ... is interaction significant?
fit<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family)+(1|Col_Field),data=dat2[!is.na(dat2$Col_Field),],family="binomial")

fit2<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$Col_Field),],family="binomial")

fit3<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family)+(1|gh_bench),data=dat2[!is.na(dat2$Col_Field),],family="binomial")

fit4<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family),data=dat2[!is.na(dat2$Col_Field),],family="binomial")

fit5<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Row_Field),data=dat2[!is.na(dat2$Col_Field),],family="binomial")

#IS column in field significant?
anova(fit,fit4) # No

#IS row in field significant?
anova(fit2,fit4) #Yes it is. 

#IS gh_bench  significant?
anova(fit3,fit4) #No.

#IS family  significant?
anova(fit5,fit2) #Yes

###Modelling fixed effects 

#IS Black path dam significant? 
fit0.1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+BlackPathDam+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$BlackPathDam),],family="binomial")
fit1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(RGR1)+(1|Family)+(1|Row_Field)+Standardize(GM_TotalLeaf_Area),data=dat2[!is.na(dat2$BlackPathDam),],family="binomial")
anova(fit0.1,fit1)# no.

#IS fern significant? 
fit0.1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$Fern),],family="binomial")
fit1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(RGR1)+(1|Family)+(1|Row_Field)+Standardize(GM_TotalLeaf_Area),data=dat2[!is.na(dat2$Fern),],family="binomial")
anova(fit0.1,fit1)# Yes

#IS Total Leaf area (first year) significant? 
fit0.1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(GM_TotalLeaf_Area)+Standardize(RGR1)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$GM_TotalLeaf_Area),],family="binomial")
fit1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(RGR1)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$GM_TotalLeaf_Area),],family="binomial")
anova(fit0.1,fit1)# no.

#IS RGR significant? 
fit0.1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+Standardize(RGR1)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$RGR1),],family="binomial")
fit1<-glmmTMB(Bolt_Survival~treatment*PCCG_1+treatment*PCCG_2+Standardize(Fern)+(1|Family)+(1|Row_Field),data=dat2[!is.na(dat2$RGR1),],family="binomial")
anova(fit0.1,fit1)# no.

#IS the interaction between treatment and PCCG_2 significant?
fit2<-update(fit1,~.-treatment:PCCG_2)
anova(fit2,fit1) #No. 


#IS PCCG_2 significant? 
fit3<-update(fit2,~.-PCCG_2)
anova(fit2,fit3) #No. 


#IS the interaction between treatment and PCCG_1 significant?
fit4<-update(fit3,~.-treatment:PCCG_1)
anova(fit4,fit3) #yes, it is. 

#Best model
fit<- glmmTMB(Bolt_Survival ~ treatment*Standardize(PCCG_1) + Standardize(Fern) +  
    (1 | Family) + (1 | Row_Field) ,data=dat2, family="binomial")
summary(fit)


#There is a significantly positive selection gradient for pccg_1 in the gm treatment only... the same is true for leaf area of the sampled leaf.  

ggplot(dat2)+
  geom_jitter(aes(y=Bolt_Survival,x=Fern))

table(dat2$Bolt_Survival,dat2$Fern)
```

