---
title: "Residuals Analysis"
author: "Mia Marcellus"
date: "4/21/2020"
output: html_document
---

Load data
```{r}
library(dplyr)
gmdata <- read.csv("DataSynthesis.csv",stringsAsFactors = F)
```

```{r}
#Assign family column
prefamily<-gsub("*.\\|","",gmdata$Tag)
gmdata$Family<-gsub("\\-.*","",prefamily)

#make a pool dataframe
pools <- gmdata %>% group_by(Family) %>% filter(Family=="pool")

#Remove maple controls
gmdata<-gmdata[!grepl("maple",gmdata$Tag,fixed=T),]

#Remove plants in fertilizer experiment and extra plants not in all treatments
gmdata <- gmdata[!grepl("i",gmdata$Sample,fixed=T),] 

#filter out intraspecific "gm" treatment
gm1 <- gmdata  %>% filter(!treatment=="gm")

#What populations are in the experiment
unique(gmdata$Family)
```

Multiply gm leaf length and width to get leaf area
```{r}
gmdata <- gmdata %>% mutate(GM_LxW = GM_Leaf_Len * GM_Leaf_Wid)
```

Eliminate pseudoreplication by averaging values for leaves of the same plant
```{r}
#Use "Tag" to group. (Tag is the unique identifyier for each plant)
nopseudo1 <- gmdata %>% group_by(Tag) %>% 
  summarise(gluc = mean(gluc_Conc),
            flav = mean(flav_Conc),
            chla = mean(ChlorA),
            chlb = mean(ChlorB),
            leafa = mean(GM_LxW),Family=first(Family),treatment=first(treatment),ThripsDam=mean(ThripsDam))#added in family collumn

#merge adds back in the pseudo replication.. you can see that there are now two values for each mean...use left_join if you want to add back in the other collumns. 
#gm <- merge(nopseudo1, gmdata, by = "Tag", all = TRUE)


#I am unsure what this is for...
#goodvarbs <- c("PlantID", "Family", "treatment", "GM_NumberOfLeaves")
#good <- gmdata %>% select(goodvarbs)

#gm1 <- merge(good, nopseudo1, by = "PlantID")

#gm1 <- unique(gm1)

#exclude pools (I am doing this for the  nopseudo dataframe.)
nopseudo1 <- nopseudo1 %>% group_by(Family) %>% filter(!Family=="pool")
```

Remove missing values
```{r}
#I took this out because the analyses and graphs will take these out automatically, and there are less flav samples than gluc samples and less gluc than chlor, etc., so we will lose power when only analysing glucs or chlor. 



#filter NAs
#gm1 <- gm1 %>% filter(!is.na(gluc), !is.na(flav), !is.na(leafa), !is.na(GM_NumberOfLeaves))
#summary(gm1)
```

Linear models
Chlorophyll and allelochemical analysis
```{r}
# chla x gluc
chlagluc <- (lm(gluc ~ chla, data = nopseudo1))

# chlb x gluc
chlbgluc <- (lm(gluc ~ chlb, data = nopseudo1))

# chla x flav
chlaflav <- (lm(flav ~ chla, data = nopseudo1))

#chlb x flav
chlbflav <- (lm(flav ~ chlb, data = nopseudo1))
```

Glucosinolates and chlorophyll
```{r}
library(ggplot2)
ggplot(nopseudo1[!is.na(nopseudo1$gluc),])+
  geom_point(aes(x = chla, y = gluc, colour = Family),
             size = 3)+
  #geom_hline(yintercept = gm1$gluc), colour = "black")+
  geom_smooth(aes(x = chla, y = gluc),
              method = "lm", se = F)+
  geom_point(aes(x = mean(chla),
                 y = mean(gluc)))+
  geom_segment(aes(x = chla, xend = chla, 
                   y = fitted(chlagluc), yend = gluc), colour = "red") 

#for each x, fitted extracts the value on the blue line
#the regression line minimizes deviations from it

#Nice graph!
```

Save residuals in dataframe
```{r}
#Creating glucosinolate data frame. This excludes NA values for glucConc
glucDat<-nopseudo1[!is.na(nopseudo1$gluc),]

chlagluc.res <-   resid(chlagluc)

glucDat$chlagluc.res <- chlagluc.res


#Double checking we added the residuals to the correct locations...

#Back calculating raw glucosinolate values
glucDat$backCalcValues<-chlagluc$fitted.values+chlagluc$residuals

#Do the back calculated values match the real values. 
any(glucDat$gluc!=glucDat$backCalcValues)
#There are discrepancies.... 

#Looking at the discrepancies, i can see that they are all just rounding errors.
glucDat[glucDat$gluc!=glucDat$backCalcValues,c("gluc","backCalcValues","Tag")]


```

Anova on resids according to population
```{r}
a1 <- lm(chlagluc.res ~ Family, data = glucDat)
summary(a1)
anova(a1)


#visualize
ggplot(glucDat, aes(x = Family, y = chlagluc.res))+
  geom_boxplot(fill = 'darkolivegreen3')+
  scale_x_discrete(name = "Population")+
  scale_y_continuous(name = "Residuals")
```


#Finding maximum genotypes with chlorophyll and leaf size controlled for. 
this can be used to determine genotypes with highest glucosinolates if mabel is planning on using new genotypes. 
```{r}
#Fitting model (This is the best model as obtained from mixed model analysis in the file "Plasticity analysis")
contrlFit<-lm(gluc~Family+chla+treatment+treatment:chla+ThripsDam,data=glucDat)

contrlFittest<-lm(gluc~chla+treatment+treatment:chla+ThripsDam,data=glucDat)

anova(contrlFit,contrlFittest) #Like the mixed model analysis, family is very significant predictor of glucosinolate concentration. 

#Checking model 
summary(contrlFit)

#Building data frame with zero thrips damage, treatment in the alone treatment only and a chlorophyll level of the mean chlorophyll level.
newframe<-glucDat %>% select(chla,Family,ThripsDam,treatment)
newframe$chla<-mean(newframe$chla)
newframe$ThripsDam<-0
newframe$treatment<-"a"

#Predicting the glucosinolate values with no thrips damage, and in no treatment. (Also extracting the standard error associated with each)
newframe$predicted<-predict.lm(contrlFit,newdata=newframe,type="response",se.fit=T)[[1]]
newframe$SE<-predict.lm(contrlFit,newdata=newframe,type="response",se.fit=T)[[2]]
#Visualizing the families with the highest glucosinolate values. 
ggplot(newframe)+
  geom_boxplot(aes(y=predicted,x=Family,colour=SE))+ylab("Glucosinolate Estimate")

newframe
#Extracting number of samples that went into relating to family estimates. 
contrlFit$coefficients


#Gluc conc is highest in alone treatment. 
```

```{r}
ggplot(glucDat[glucDat$treatment=="a",])+
  geom_jitter(aes(x=Family,y=gluc,colour=Family))

ggplot(glucDat[glucDat$treatment=="m",])+
  geom_jitter(aes(x=Family,y=gluc,colour=Family))

```

#If Mabel wants to use genotypes from my project, these are the ones with the highest gluc conc in the alone treatment. 
```{r}
gmdata <- read.csv("DataSynthesis.csv",stringsAsFactors = F)

#Assign family column
prefamily<-gsub("*.\\|","",gmdata$Tag)
gmdata$Family<-gsub("\\-.*","",prefamily)

#make a pool dataframe
pools <- gmdata %>% group_by(Family) %>% filter(Family=="pool")

#Remove maple controls
gmdata<-gmdata[!grepl("maple",gmdata$Tag,fixed=T),]

#Remove plants in fertilizer experiment and extra plants not in all treatments
gmdata <- gmdata[!grepl("i",gmdata$Sample,fixed=T),] 

#filter out intraspecific "gm" treatment
gm1 <- gmdata  %>% filter(!treatment=="gm")

#What populations are in the experiment
unique(gmdata$Family)
```

Multiply gm leaf length and width to get leaf area
```{r}
gmdata <- gmdata %>% mutate(GM_LxW = GM_Leaf_Len * GM_Leaf_Wid)
```

Eliminate pseudoreplication by averaging values for leaves of the same plant
```{r}
#Use "Tag" to group. (Tag is the unique identifyier for each plant)
nopseudo1 <- gmdata %>% group_by(Tag) %>% 
  summarise(gluc = mean(gluc_Conc),
            flav = mean(flav_Conc),
            chla = mean(ChlorA),
            chlb = mean(ChlorB),
            leafa = mean(GM_LxW),Family=first(Family),treatment=first(treatment),ThripsDam=mean(ThripsDam))#added in family collumn

```




#Flavnoids did not have family as a significant predictor, so i would not look at those to determine which one to use. 

